### 2018-04-06 paper.tex
Cleanup

\documentclass{IOS-Book-Article}

\usepackage{mathptmx}

%\usepackage{times}
%\normalfont
\usepackage[T1]{fontenc}
%\usepackage[mtplusscr,mtbold]{mathtime}
%
\begin{document}
\begin{frontmatter}              % The preamble begins here.

%\pretitle{Pretitle}
\title{LV2}
\runningtitle{LV2}
%\subtitle{Subtitle}

%\author[A]{\fnms{First} \snm{Last}%
%\thanks{Corresponding Author: Book Production Manager, IOS Press, Nieuwe Hemweg 6B,
%1013 BG Amsterdam, The Netherlands; E-mail:
%bookproduction@iospress.nl.}},
%\author[B]{\fnms{Second} \snm{Author}}
%and
%\author[B]{\fnms{Third} \snm{Author}}

%\runningauthor{B.P. Manager et al.}
%\address[A]{Somewhere, Some Country}
%\address[B]{Short Affiliation of Second Author and Third Author}

%\begin{abstract}
%
%\end{abstract}

\begin{keyword}
Corpus Linguistics \sep Latvian \sep Russian \sep English
\end{keyword}
\end{frontmatter}

\thispagestyle{empty}
\pagestyle{empty}

\section*{Introduction}

\section{Typographical Style and Layout}

\end{document}

### 2018-04-10 paper.tex
Intro

@@
 \documentclass{IOS-Book-Article}
+
+\usepackage[square,numbers,sort]{natbib}
+
+\usepackage{color}
+\usepackage[pdfusetitle]{hyperref}
+% http://colorschemedesigner.com/#4o42FfqublRMS
+\definecolor{linkcolor}{RGB}{66, 54, 122}
+\definecolor{citecolor}{RGB}{84, 141, 100}
+\definecolor{urlcolor}{RGB}{168, 70, 67}
+\hypersetup{
+  colorlinks=true,
+  linkcolor=linkcolor,
+  citecolor=citecolor,
+  urlcolor=urlcolor,
+}
+
+\usepackage{todonotes}
 
@@
 
-%\author[A]{\fnms{First} \snm{Last}%
-%\thanks{Corresponding Author: Book Production Manager, IOS Press, Nieuwe Hemweg 6B,
-%1013 BG Amsterdam, The Netherlands; E-mail:
-%bookproduction@iospress.nl.}},
+\author[A]{\fnms{Anonymous} \snm{Submission}%
+\thanks{Corresponding Author: Book Production Manager, IOS Press, Nieuwe Hemweg 6B,
+1013 BG Amsterdam, The Netherlands; E-mail:
+bookproduction@iospress.nl.}}
 %\author[B]{\fnms{Second} \snm{Author}}
 %and
-%\author[B]{\fnms{Third} \snm{Author}}
+%\author[B]{\fnms{Third} \snm{Author}
 
 %\runningauthor{B.P. Manager et al.}
-%\address[A]{Somewhere, Some Country}
+\address[A]{Confidential Review Copy, Do Not Distribute}
 %\address[B]{Short Affiliation of Second Author and Third Author}
@@
 
-\section{Typographical Style and Layout}
+The paper present a multilingual, location-anchored corpus of tweets from Latvia.
+A difficulty of collecting a socially representative corpus from the country is that several languages are used there: Latvian is the main communication language, Russian is the language of the largest minority in Latvia and English is widely used.
+There are several challenges of building a tweet collection that adequately represents language use in the country.
+
+Building a monolingual Latvian collection can be done by harvesting tweets that contain indicative Latvian words which do not present in other languages, similarly how it is done for Dutch \cite{sang2013}.
+However, such an approach does not fit for Russian tweets because tweets that originate from Russia will inevitably collected.
+It is the same for English, where tweets from all around the world will be collected.
+For the same reason the TREC-like collection building approach \todo{citation} of filtering the publicly available stream of tweets by language does not work.
+
+Geo-location based collection produces good results \cite{milajevs:2017:BUCC}, but a large number of tweets is not geo-located which makes retrieval incomplete, but most representative.
+%
+Tweet collection based on a curated list of users \cite{SANVICENTE16.465} is effective but more based than the geo-located approach.
+
+\bibliographystyle{unsrtnat}
+\bibliography{references,dmilajevs_publications}
 

### 2018-04-18 paper.tex
Intro edits

--- 2018-04-06 paper.tex
@@
 
-\section{Typographical Style and Layout}
+This paper presents a multilingual, location-anchored corpus of tweets from Latvia.
+The main challenge of collecting a socially representative corpus from the country is that several languages are used there: Latvian, the main communication language, Russian, the language of the largest minority in Latvia, and English.
+
+%There are several challenges of building a tweet collection that adequately represents language use in the country.
+%
+Building a monolingual Latvian collection could be done by harvesting tweets that contain indicative Latvian words which do not present in other languages, similarly how it is done for Dutch \cite{sang2013}.
+However, such an approach is not suitable for Russian tweets, because tweets that originate from Russia and other countries would inevitably be collected, and English, because of the same issue, but on a much larger scale.
+%
+For the same reason, a TREC-like collection building approach \cite{lin2016overview} of filtering the publicly available stream of tweets by language would not work.
+%
+A tweet collection based on a curated list of users \cite{SANVICENTE16.465} is effective but might lead to a biased collection if the list is not diverse.
+Also, tracking personal accounts is problematic because of privacy concerns.
+%
+A geo-location based collection procedure produces representative results \cite{milajevs:2017:BUCC}.
+It is not biased linguistically because it is based neither on a list of keywords nor on a list of users.
+Unfortunately, a large number of tweets is not geo-located, which makes retrieval incomplete.
+
+\bibliographystyle{unsrtnat}
+\bibliography{references,dmilajevs_publications}
 

### 2018-04-18 paper.tex
Intro: method

@@
 
+%%%%%%%%%
+% Problem
+%%%%%%%%%
 %There are several challenges of building a tweet collection that adequately represents language use in the country.
@@
 
+%%%%%%%%%%
+% Solution
+%%%%%%%%%%
+To keep a balance between completeness and objectivity, this work applies a hybrid approach by combining a geo-location based collection procedure with tracking a curated list of users.
+To minimize privacy issues, only accounts of major local newspapers, government, sport clubs, and businesses are tracked.
+The list is made to cover a broad variety of entities in order to produce an unbiased collection.
+Moreover, if a popular entity is skipped, the tweets produced by it should be included by the geo-location, based method because of retweets, and it will be mentioned by other people.
+
+%%%%%%%%%
+% Results
+%%%%%%%%%
+
+%%%%%%%%%%%%%
+% So, what...
+%%%%%%%%%%%%%
+
 \bibliographystyle{unsrtnat}

### 2018-04-19 paper.tex
Tweet collection procedure

--- 2018-04-18 paper.tex
@@
 
-\usepackage{todonotes}
-
+\usepackage{soul}
+\definecolor{hlcolor}{RGB}{255, 221, 163}
+\sethlcolor{hlcolor}
 \usepackage{mathptmx}
@@
 Building a monolingual Latvian collection could be done by harvesting tweets that contain indicative Latvian words which do not present in other languages, similarly how it is done for Dutch \cite{sang2013}.
-However, such an approach is not suitable for Russian tweets, because tweets that originate from Russia and other countries would inevitably be collected, and English, because of the same issue, but on a much larger scale.
+However, such an approach is not suitable for tweets in Russian and English, as these languages are widely used outside of Latvia.
 %
@@
 
+%%%%%%%%
+% Method
+%%%%%%%%
+To keep a balance between privacy and objectivity maximizing completeness, this work applies a hybrid approach by combining a geo-location based collection procedure with tracking a curated list of users.
+To minimize privacy issues, only accounts of organizations and public figures are tracked.
+
+%%%%%%%%%
+% Results
+%%%%%%%%%
+
+%%%%%%%%%%%%%
+% So, what...
+%%%%%%%%%%%%%
+
+\section{Data collection}
+\label{sec:data-collection}
+
+Over the period from 15 April 2017 to \hl{19 April 2018} the initial set of \hl{1\,685\,048} tweets were collected from the \texttt{POST status/filter} endpoint of the Twitter Streaming API.\footnotemark{}
+%
+\footnotetext{\url{https://developer.twitter.com/en/docs/tweets/filter-realtime/api-reference/post-statuses-filter}}
+%
+The \texttt{locations} parameter was set to the bounding box of Riga, the capital of Latvia.\footnotemark{}
+%
+\footnotetext{The coordinates of the bounding box are \texttt{23.9325829, 56.8570671, 24.3247299, 57.0859184}.}
+%
+In addition to the location, \hl{420} accounts were tracked. \hl{The whole list of screen names together with user ID is available in the supplement.}
+
+To comply with Twitter's terms of service, on \hl{19 April 2018}, the raw tweet data was redownloaded (or rehydrated) to get rid of deleted tweets.
+In addition to that, the tweets that originated a retweet were added to the collection.
+Also, we have noticed a large number of tweets that come from Sweden (probably because of the imprecise \texttt{locations} parameter value), so the tweets which location country code was \texttt{SE} were omitted.
+This resulted in \hl{1\,133\,812} tweets that formed the final collection presented here.
+
 \bibliographystyle{unsrtnat}

### 2018-04-24 paper.tex

@@
 This paper presents a multilingual, location-anchored corpus of tweets from Latvia.
-The main challenge of collecting a socially representative corpus from the country is that several languages are used there: Latvian, the main communication language, Russian, the language of the largest minority in Latvia, and English.
+The main challenge of collecting a socially representative corpus from this country is that several languages are used there: Latvian, the main communication language, Russian, the language of the largest minority in Latvia, and English.
 
@@
 %
-Building a monolingual Latvian collection could be done by harvesting tweets that contain indicative Latvian words which do not present in other languages, similarly how it is done for Dutch \cite{sang2013}.
+Building a monolingual Latvian collection could be done by harvesting tweets that contain indicative Latvian words which do not present in other languages, similarly to how it is done for Dutch \cite{sang2013}.
 However, such an approach is not suitable for tweets in Russian and English, as these languages are widely used outside of Latvia.
@@
 %
-A tweet collection based on a curated list of users \cite{SANVICENTE16.465} is effective but might lead to a biased collection if the list is not diverse.
-Also, tracking personal accounts is problematic because of privacy concerns.
+A tweet collection based on a curated list of users \cite{SANVICENTE16.465} is effective, but extra care must be taken as tracking personal accounts might problematic due to privacy concerns.
 %
-A geo-location based collection procedure produces representative results \cite{milajevs:2017:BUCC}.
-It is not biased linguistically because it is based neither on a list of keywords nor on a list of users.
-Unfortunately, a large number of tweets is not geo-located, which makes retrieval incomplete.
+A geo-location based collection produces representative results \cite{milajevs:2017:BUCC}.
+It is not biased linguistically because it is not based on a list of keywords.
+It is not biased thematically because it is not based on a list of users.
+However, a large number of tweets is not geo-located, which makes retrieval incomplete.
 
@@
 
-Over the period from 15 April 2017 to \hl{19 April 2018} the initial set of \hl{1\,685\,048} tweets were collected from the \texttt{POST status/filter} endpoint of the Twitter Streaming API.\footnotemark{}
+Over the period from 15 April 2017 to \hl{19 April 2018} the initial set of \hl{1\,685\,048} tweets was collected from the \texttt{POST status/filter} endpoint of the Twitter Streaming API.\footnotemark{}
 %
@@
 To comply with Twitter's terms of service, on \hl{19 April 2018}, the raw tweet data was redownloaded (or rehydrated) to get rid of deleted tweets.
-In addition to that, the tweets that originated a retweet were added to the collection.
+The tweets that originated a retweet were added to the collection.
 Also, we have noticed a large number of tweets that come from Sweden (probably because of the imprecise \texttt{locations} parameter value), so the tweets which location country code was \texttt{SE} were omitted.

### 2018-04-24 paper.tex
Source statistics

@@
 \usepackage[square,numbers,sort]{natbib}
+
+\usepackage{booktabs}
+\usepackage{multirow}
 
@@
 %
-A tweet collection based on a curated list of users \cite{SANVICENTE16.465} is effective, but extra care must be taken as tracking personal accounts might problematic due to privacy concerns.
+A tweet collection based on a curated list of users \cite{SANVICENTE16.465} is effective, but extra care must be taken as tracking personal accounts might be problematic due to privacy concerns.
 %
@@
 The tweets that originated a retweet were added to the collection.
-Also, we have noticed a large number of tweets that come from Sweden (probably because of the imprecise \texttt{locations} parameter value), so the tweets which location country code was \texttt{SE} were omitted.
+Also, we have noticed a large number of tweets that came from Sweden (probably because of the imprecise \texttt{locations} parameter value), so the tweets which location country code was \texttt{SE} were omitted.
 This resulted in \hl{1\,133\,812} tweets that formed the final collection presented here.
+
+\section{GLobal analysis}
+\label{sec:global-analysis}
+
+\input{figures/rehydrated_tweets_source_counts.tex}
+
+On average, about \hl{3\,000} tweets were collected per day, which is more than \hl{1\,500} by the geo-location based technique in \cite{milajevs:2017:BUCC}.
 

### 2018-04-24 paper.tex
Initial global analysis.

@@
 %
+
+\newcommand{\sn}[1]{\href{https://twitter.com/#1}{\texttt{@#1}}}
+
 \begin{document}
@@
 
-\section{GLobal analysis}
+\section{Global analysis}
 \label{sec:global-analysis}
@@
 
-On average, about \hl{3\,000} tweets were collected per day, which is more than \hl{1\,500} by the geo-location based technique in \cite{milajevs:2017:BUCC}.
+On average, about \hl{3\,200} tweets were collected per day, which is more than \hl{1\,500} by the geo-location based technique in \cite{milajevs:2017:BUCC}.
+Most of the tweets came from the official Twitter clients for Web, Android or iPhone.
+Together these clients contributed more than 60\% of all collected tweets, refer to Table~\ref{tab:source_counts} for more details.
+
+The twitter web client is used by both: the general public and media companies.
+The top 5 of most active accounts consists only of tracked Latvian media accounts: \sn{DienaLV}, a newspaper, \sn{LA\_lv}, another newspaper, \sn{JaunsLV}, a media portal, \sn{TV3\_Play}, a TV channel, and \sn{dblv}, a newspaper.
+
+Notably, for mobile clients, the majority of tweets comes from the general public, because they are either geo-located or mention a tracked account.
+The number of tweets coming from tracked accounts, \hl{that are mostly media}, is lower for Android \hl{(8.5\%)} than for iPhone \hl{(13.5\%)}.
+The difference can be explained by the fact, that all top 5 Android users are personal accounts, while for iPhone there are only 2 personal accounts in the top 5.
+\sn{TV3zinas}, a news account of a TV channel, tweets the most from iPhone.
+\sn{Lattelecom}, a telecommunication company, is the second most active iPhone user.
+\sn{AstrologiLv} writes about astrology and is the fourth most active iPhone user.
+All three accounts tweet exclusively in Latvian and were tracked during corpus collection.
+
+Client applications that produce tweets mostly from tracked accounts are used by the media.
+For the TweetDeck, TVNET Login, dlvr.it and SKATIES client applications the top 5 users are tracked media accounts that write dominantly in Latvian.
+The exceptions are a business account \sn{Kompresori} that was not tracked and tweets in three languages: Latvian, Russian and English, \sn{RusApollo} and \sn{TVNET\_rus} who tweet identical content exclusively in Russian, and \sn{SejasLV}, an exclusively Latvian account writing about celebrities that was not tracked.
+
+TweetDeck is used by \sn{DelfiLV}, a major media portal, \sn{LV\_Portals}, an account run by the official government gazette of the Republic of Latvia, \sn{lsmlv}, an account of a publicly funded radio and television organization (LSM), \sn{ltvzinas}, the news account of Latvian Television, \sn{RietumuRadio}, a radio station.
+
+TVNET is a media company that controls several media portals.
+The most active accounts that use their application are \sn{TVnet\_portals}, \sn{RusApollo}, \sn{TVnet\_rus}, \sn{SportsTVNET}, and \sn{SejasLV}.
+
+The tweet delivery service \texttt{dlvr.it} is used by the newspaper \sn{nralv} and their sport portal \sn{Sportacentrs}, the photo account of the national news agency (LETA) \sn{letafoto}, \sn{Kompresori} and the sport account of Latvian Television \sn{ltvsports}.
+
+SKATIES delivers video content from several sources. The most active accounts are \sn{skatieslatvija}, \sn{lnt\_lv}, \sn{tv3lv}, \sn{BezTabuTV3} and \sn{TV3Zinas}.
+
+Some tweets come from social media networks.
+Facebook content mostly comes from tracked media accounts.
+The top 5 most active users are: \sn{mixnews\_lv}, the Russian edition of a media portal, \sn{Otkrito}, also the Russian edition of \sn{JaunsLV}, \sn{labdienlv}, \sn{ekonimikalv} and \sn{nozare}, all three belonging to one Latvian media portal.
+The fact that Russian accounts are not active among other clients might suggest that Russian content is not spread via Twitter, but, for example, via Facebook.
+
+The content that comes form Foursquare and Instagram is created by the general public.
+
+There is a clear pattern that mobile clients are used by personal accounts, while media companies set up a special solution to deliver tweets, probably, integrating it with their content delivery systems or simply using a web client from an office machine.
 

### 2018-05-09 paper.tex
Language

@@
 \documentclass{IOS-Book-Article}
+
+\usepackage{graphicx}
 
@@
 
-\section{Global analysis}
+\section{Twitter users}
 \label{sec:global-analysis}
@@
 For the TweetDeck, TVNET Login, dlvr.it and SKATIES client applications the top 5 users are tracked media accounts that write dominantly in Latvian.
-The exceptions are a business account \sn{Kompresori} that was not tracked and tweets in three languages: Latvian, Russian and English, \sn{RusApollo} and \sn{TVNET\_rus} who tweet identical content exclusively in Russian, and \sn{SejasLV}, an exclusively Latvian account writing about celebrities that was not tracked.
+The exceptions are a business account \sn{Kompresori} that was not tracked and tweets in three languages: Latvian, Russian and English, \sn{RusApollo} and \sn{TVNET\_rus} who tweet identical content exclusively in Russian, and \sn{SejasLV}, an exclusively Latvian account writing about celebrities, which was not tracked.
 
@@
 The top 5 most active users are: \sn{mixnews\_lv}, the Russian edition of a media portal, \sn{Otkrito}, also the Russian edition of \sn{JaunsLV}, \sn{labdienlv}, \sn{ekonimikalv} and \sn{nozare}, all three belonging to one Latvian media portal.
-The fact that Russian accounts are not active among other clients might suggest that Russian content is not spread via Twitter, but, for example, via Facebook.
+The fact that Russian accounts are not active among other clients might suggest that Russian content is not spread via Twitter, but via Facebook.
 
@@
 
+\section{Language}
+\label{sec:language}
+
+Latvian is the dominant language: \hl{880\,351 (74\%)} tweets are written in it.\footnotemark{} There are \hl{12\,505 (11\%)} tweets in Russian, \hl{116203 (10\%)} in English and \hl{66\,969 (6\%)} in other languages.
+Figure~\ref{fig:rehydrated-tweets-count-by-day} shows the tweet volume over time.
+
+Latvian dominates almost in every client application.
+Tweets coming from Foursquare are labeled as Latvian in \hl{78\%} cases (see Table~\ref{tab:source_counts}), that might be due to Latvian location names.
+
+Russian tweets constitute of more then half tweets coming from TVNET, where its share is \hl{52\%} while Latvian is \hl{46.3\%}, and from Facebook, where the two most active users are Russian madia.
+
+A lot of English content is coming form Instagram (\hl{32.9\%}), that might be due to the dominance of hashtags over other text.
+Also, there are many tweets labeled as written in other languages that come from Foursquare and Instagram.
+As Instagram posts are more likely to contain hashtags and Foursqure tweets contain location names, tweets should not be assigned a single language label, but instead be labeled as written in several languages.
+
+\footnotetext{Twitter labels tweets with the language they are written in.}
+
+\input{figures/rehydrated_tweets_count_by_day.tex}
+
 \bibliographystyle{unsrtnat}

### 2018-05-09 paper.tex
Topics

@@
 
+\footnotetext{Twitter labels tweets with the language they are written in.}
+
 Latvian dominates almost in every client application.
@@
 
-\footnotetext{Twitter labels tweets with the language they are written in.}
+\section{Topics}
+\label{sec:topics}
+
+To investigate the collection further nine topics of interests were defined. The collection was manually searched using keywords to get relevant tweets. The topics are
+\begin{itemize}
+\item \texttt{LV001: Winter} Everything about winter. The relevant tweets are mostly about the weather, the pictures of snow and driving conditions.
+\item \texttt{LV002: Mel\=anijas hronika} Mel\=anijas hronika is a Latvian movie that was selected for Foreign-Language Category for Oscars.
+\item \texttt{LV003: Refugees} A broad topic about refugee crisis in Europe, attitude to immigration and immigrants.
+\item \texttt{LV004: Dv\=eese\c{l}u putenis} A Latvian movie that is currently in production.
+\item \texttt{LV005: Hockey} Ice hockey related tweets.
+\item \texttt{LV006: Christmas} Christmas.
+\item \texttt{LV007: New Year} New Year.
+\item \texttt{LV008: Olympics} Tweets about the Olympic games and the Latvian team.
+\item \texttt{LV009: Brexit} Brexit.
+\end{itemize}
 

### 2018-05-10 paper.tex
Topics
First complete draft

@@
 %
-In addition to the location, \hl{420} accounts were tracked. \hl{The whole list of screen names together with user ID is available in the supplement.}
+In addition to the location, \hl{420} accounts were tracked. %\hl{The whole list of screen names together with user ID is available in the supplement.}
 
@@
 
+\input{figures/rehydrated_tweets_count_by_day.tex}
+
 Latvian is the dominant language: \hl{880\,351 (74\%)} tweets are written in it.\footnotemark{} There are \hl{12\,505 (11\%)} tweets in Russian, \hl{116203 (10\%)} in English and \hl{66\,969 (6\%)} in other languages.
@@
 
-To investigate the collection further nine topics of interests were defined. The collection was manually searched using keywords to get relevant tweets. The topics are
+To investigate the collection further nine topics of interests were defined. The collection was manually searched using keywords to get relevant tweets. The topics are:
 \begin{itemize}
-\item \texttt{LV001: Winter} Everything about winter. The relevant tweets are mostly about the weather, the pictures of snow and driving conditions.
+\item \texttt{LV001: Winter} Everything about winter.
 \item \texttt{LV002: Mel\=anijas hronika} Mel\=anijas hronika is a Latvian movie that was selected for Foreign-Language Category for Oscars.
@@
 \item \texttt{LV004: Dv\=eese\c{l}u putenis} A Latvian movie that is currently in production.
-\item \texttt{LV005: Hockey} Ice hockey related tweets.
+\item \texttt{LV005: Ice hockey} Ice hockey related tweets.
 \item \texttt{LV006: Christmas} Christmas.
@@
 
-\input{figures/rehydrated_tweets_count_by_day.tex}
+Topics exhibit various temporal patterns, refer to Figure~\ref{fig:topic_timeline}. The volume of tweets is constant for long-lasting news stories such as the refugee crisis, Brexit and ice hockey.
+%
+During the Ice Hockey World Championship the volume of hockey related tweets increases.
+Similarly, event-based topics---such as Christmas, New Year and Olympics---are the most active during corresponding events, the volume of tweets slowly builds up as an event approaches.
+
+In case of Christmas, we see unexpected activity in March which is due to the discussion of making the Orthodox Christmas a public holiday in Parliament.
+This topic exhibits some cultural differences and language use.
+Tweets in Latvian peak during Advent and Christmas in December, tweets in Russian reach maximum both in December and early January when Orthodox Christmas are celebrated.
+It worth noting that during the discussion whether Orthodox Christmas should be a public holiday, it sometimes was referred as ``Russian Christmas''.
+
+Topics about movies are the smallest volume-wise.
+For a movie that was shown at several international festivals, we see multilingual content, while tweets about a movie that is still in production are solely monolingual.
+
+The topic about Winter is an example of a seasonal topic, which is mostly about the weather, the pictures of snow and driving conditions.
+
+Table~\ref{tab:topic_lang_counts} shows the total number of tweets per topic and language share for Latvian, Russian and English.
+For all topics the share of Latvian tweets is higher than on average in the collection (Section~\ref{sec:language}).
+For Russian and English these numbers are generally lower than global average.
+
+The most notable exception being Russian tweets about New Year, probably because of the content written by Russian tourists.
+The topic about Winter comes close for Russian with respect to the expected average, but is low for English tweets.
+Interestingly, for the international news topics, there is proportionally more English content about Brexit than about refugees.
+
+\input{figures/topic_lang_counts.tex}
+
+\section{Conclusion and future work}
+\label{sec:conclusion}
+
+This paper presents a multilingual tweet collection with some analysis of users, language use and content.
+The analysis reveal that the resource might be used in several areas ranging from computational linguistics, information retrieval and social science.
+
+As for computational linguistics, multilingual language identification needs to be applied to it, as tweets are not always monolingual, as we indirectly showed by the large volume of English tweets coming from Instagram and Latvian tweets coming from Foursquare.
+
+An evidence of the existence of reliable topics that exhibit various temporal patterns could be exploited in information retrieval either for evaluation of multilingual retrieval systems or development of collection exploration techniques.
+
+For social analysis, it would be nice to see what topics are multilingual, for example Winter, and what topics are monolingual, for example movie related topics in this work, and why the topics are discussed differently depending on a language.
+
+\input{figures/topic_timeline.tex}
 

### 2018-05-11 paper.tex
Comments

@@
 It is not biased thematically because it is not based on a list of users.
-However, a large number of tweets is not geo-located, which makes retrieval incomplete.
+However, a large number of tweets are not geo-located, which makes retrieval incomplete.
+% IMS self-cite alert. What's new in this work?
 
@@
 To minimize privacy issues, only accounts of organizations and public figures are tracked.
+
+% IMS it's worth saying in one sentence how you will determine that the final collection has the properties you desire.
 
@@
 In addition to the location, \hl{420} accounts were tracked. %\hl{The whole list of screen names together with user ID is available in the supplement.}
+% IMS how did you select those accounts?
+Can you describe them generically here?
+(i.e.
+"Latvian news outlets, famous actors and politicians, and a selection of Eurovision finalists.")  You should make clear you hand picked them based on background knowledge or if this list was scraped from a public resource, since it reflects effort put into making the collection.
 
@@
 This resulted in \hl{1\,133\,812} tweets that formed the final collection presented here.
+% IMS I think "hydrate" is a jargon term that twarc invented but that isn't widely used.
 
@@
 
-The twitter web client is used by both: the general public and media companies.
+The twitter web client is used by both the general public and media companies.
 The top 5 of most active accounts consists only of tracked Latvian media accounts: \sn{DienaLV}, a newspaper, \sn{LA\_lv}, another newspaper, \sn{JaunsLV}, a media portal, \sn{TV3\_Play}, a TV channel, and \sn{dblv}, a newspaper.
@@
 Client applications that produce tweets mostly from tracked accounts are used by the media. 
+% IMS I don't understand the previous sentence
 For the TweetDeck, TVNET Login, dlvr.it and SKATIES client applications the top 5 users are tracked media accounts that write dominantly in Latvian.
 The exceptions are a business account \sn{Kompresori} that was not tracked and tweets in three languages: Latvian, Russian and English, \sn{RusApollo} and \sn{TVNET\_rus} who tweet identical content exclusively in Russian, and \sn{SejasLV}, an exclusively Latvian account writing about celebrities, which was not tracked.
+
+% IMS terminology jumble.
+You are tracking, and also other users are tracking, and you selected users who were tracking (well, actually, probably retweeting) tweets from accounts you were tracking already.
+You want this section to read like a recipe for your reader who wants to duplicate your effort in Swahili or whatever.
 
@@
 The fact that Russian accounts are not active among other clients might suggest that Russian content is not spread via Twitter, but via Facebook.
+% IMS but you said you were tracking Facebook.  I think you mean that you can only track FB when the content is also posted to Twitter, but not otherwise.
 
-The content that comes form Foursquare and Instagram is created by the general public.
+The content that comes from Foursquare and Instagram is created by the general public.
 
 There is a clear pattern that mobile clients are used by personal accounts, while media companies set up a special solution to deliver tweets, probably, integrating it with their content delivery systems or simply using a web client from an office machine.
+
+% IMS I wonder if a flow diagram would illustrate the paths this information takes before it gets on Twitter.
 
@@
 
+% IMS the point of the paper is that you believe this is a more representative sample than would be obtained by simpler methods.  Why do you believe it?  Is the hypothesis falsifiable?
+
+% IMS is there code-switching?  How are you deciding that a tweet is in one language vs another?
+
 \section{Topics}
@@
 
+% IMS I note your topics are titled either in Latvian or English.
+Is that intentional?
+Does it reflect a goal of boosting content from those languages?
+Bigger question: why these topics?
+More esoteric question: what value are the topics adding to your collection?
+How many topics should you have?
 Topics exhibit various temporal patterns, refer to Figure~\ref{fig:topic_timeline}. The volume of tweets is constant for long-lasting news stories such as the refugee crisis, Brexit and ice hockey.
@@
 
+% IMS The conclusion does not address any of the questions raised in the abstract/introduction.
+
 This paper presents a multilingual tweet collection with some analysis of users, language use and content.

### 2018-05-11 paper.tex
Getting ready for the submission.

@@
 
-\usepackage{soul}
-\definecolor{hlcolor}{RGB}{255, 221, 163}
-\sethlcolor{hlcolor}
+%\usepackage{soul}
+%\definecolor{hlcolor}{RGB}{255, 221, 163}
+%\sethlcolor{hlcolor}
+\newcommand{\hl}[1]{#1}
+
 \usepackage{mathptmx}
@@
 %
-A geo-location based collection produces representative results \cite{milajevs:2017:BUCC}.
-It is not biased linguistically because it is not based on a list of keywords.
-It is not biased thematically because it is not based on a list of users.
+%A geo-location based collection produces representative results \cite{milajevs:2017:BUCC}.
+%
+An alternative approach would be to retrieve only geo-located tweets.
+Such a collection would neither be biased linguistically because it is not based on a list of keywords, nor it would be biased thematically because it is not based on a list of users.
 However, a large number of tweets are not geo-located, which makes retrieval incomplete.
@@
 
+Our base assumption is that geo-located tweets is a representative and unbiased sample of Latvian Twitter.
+Thus, an extended collection should exhibit similar properties as the geo-located one.
+The main property we are interested in this work is the language proportion.
+We hypothesize, that an unbiased extended collection should have similar language distribution as the initial.
+
+To study the collection in more details, we defined 9 topics and manually search for relevant tweets.
+
 %%%%%%%%%
@@
 %%%%%%%%%
+
+The analysis of the collection shows that it is biased toward content in Latvian: proportionally there are more tweets in Latvian than in Russian and English.
+Also, Latvian is more dominant language than expected in all but one topic, the exception being the topic about New Year celebration.
 
@@
 
+Building an unbiased collection is difficult.
+In our case the main reason of introduced bias, might be that Russian and English content is less news-oriented and much more informal.
+In other words, while it's common to discuss current news in Latvian by engaging with media, the tweets in Russian and English might be more personal and friend-oriented.
+
 \section{Data collection}
@@
 
-Over the period from 15 April 2017 to \hl{19 April 2018} the initial set of \hl{1\,685\,048} tweets was collected from the \texttt{POST status/filter} endpoint of the Twitter Streaming API.\footnotemark{}
+Over the period from 15 April 2017 to \hl{8 May 2018} the initial set of \hl{1\,708\,236} tweets was collected from the \texttt{POST status/filter} endpoint of the Twitter Streaming API.%\footnotemark{}
 %
-\footnotetext{\url{https://developer.twitter.com/en/docs/tweets/filter-realtime/api-reference/post-statuses-filter}}
+%\footnotetext{\url{https://developer.twitter.com/en/docs/tweets/filter-realtime/api-reference/post-statuses-filter}}
 %
-The \texttt{locations} parameter was set to the bounding box of Riga, the capital of Latvia.\footnotemark{}
+The \texttt{locations} parameter was set to the bounding box of Riga, the capital of Latvia.%\footnotemark{}
 %
-\footnotetext{The coordinates of the bounding box are \texttt{23.9325829, 56.8570671, 24.3247299, 57.0859184}.}
+%\footnotetext{The coordinates of the bounding box are \texttt{23.9325829, 56.8570671, 24.3247299, 57.0859184}.}
 %
-In addition to the location, \hl{420} accounts were tracked. %\hl{The whole list of screen names together with user ID is available in the supplement.}
+In addition to the location, 420 accounts were tracked.%\footnotemark{} %\hl{The whole list of screen names together with user ID is available in the supplement.}
+%\footnotetext{In this paper, by ``tracking users'', we mean that their user IDs where passed to the Twitter API to collect tweets that they created, or the tweets that are replies by other users to their tweets.
+Refer to \url{https://developer.twitter.com/en/docs/tweets/filter-realtime/guides/basic-stream-parameters\#follow} for a complete description.
+Keep in mind that this is different from the case when a user follows another user.}
+%
+The accounts are mostly Latvian (that is, coming from Latvia, but not necessary produce content in Latvian) news outlets, politicians, businesses, artists and sport clubs.
+
 % IMS how did you select those accounts?
@@
 
-To comply with Twitter's terms of service, on \hl{19 April 2018}, the raw tweet data was redownloaded (or rehydrated) to get rid of deleted tweets.
+%To comply with Twitter's terms of service, on \hl{8 May 2018}, the raw tweet data was redownloaded to get rid of deleted tweets.
 The tweets that originated a retweet were added to the collection.
 Also, we have noticed a large number of tweets that came from Sweden (probably because of the imprecise \texttt{locations} parameter value), so the tweets which location country code was \texttt{SE} were omitted.
-This resulted in \hl{1\,133\,812} tweets that formed the final collection presented here.
+This resulted in \hl{1\,242\,943} tweets that formed the final collection presented here.
 % IMS I think "hydrate" is a jargon term that twarc invented but that isn't widely used.
@@
 
-On average, about \hl{3\,200} tweets were collected per day, which is more than \hl{1\,500} by the geo-location based technique in \cite{milajevs:2017:BUCC}.
+On average, about \hl{3\,200} tweets were collected per day, which is more than 1\,500 by the geo-location based technique in \cite{milajevs:2017:BUCC}.
 Most of the tweets came from the official Twitter clients for Web, Android or iPhone.
@@
 Notably, for mobile clients, the majority of tweets comes from the general public, because they are either geo-located or mention a tracked account.
-The number of tweets coming from tracked accounts, \hl{that are mostly media}, is lower for Android \hl{(8.5\%)} than for iPhone \hl{(13.5\%)}.
+The number of tweets coming from tracked accounts, that are mostly media, is lower for Android \hl{(8.4\%)} than for iPhone \hl{(13.8\%)}.
 The difference can be explained by the fact, that all top 5 Android users are personal accounts, while for iPhone there are only 2 personal accounts in the top 5.
@@
 
-Client applications that produce tweets mostly from tracked accounts are used by the media. 
+%Client applications that produce tweets mostly from tracked accounts are used by the media. 
 % IMS I don't understand the previous sentence
-For the TweetDeck, TVNET Login, dlvr.it and SKATIES client applications the top 5 users are tracked media accounts that write dominantly in Latvian.
+%For the TweetDeck, TVNET Login, dlvr.it and SKATIES client applications the top 5 users are tracked media accounts that write dominantly in Latvian.
 The exceptions are a business account \sn{Kompresori} that was not tracked and tweets in three languages: Latvian, Russian and English, \sn{RusApollo} and \sn{TVNET\_rus} who tweet identical content exclusively in Russian, and \sn{SejasLV}, an exclusively Latvian account writing about celebrities, which was not tracked.
@@
 
-TweetDeck is used by \sn{DelfiLV}, a major media portal, \sn{LV\_Portals}, an account run by the official government gazette of the Republic of Latvia, \sn{lsmlv}, an account of a publicly funded radio and television organization (LSM), \sn{ltvzinas}, the news account of Latvian Television, \sn{RietumuRadio}, a radio station.
+%TweetDeck is used by \sn{DelfiLV}, a major media portal, \sn{LV\_Portals}, an account run by the official government gazette of the Republic of Latvia, \sn{lsmlv}, an account of a publicly funded radio and television organization (LSM), \sn{ltvzinas}, the news account of Latvian Television, \sn{RietumuRadio}, a radio station.
 
-TVNET is a media company that controls several media portals.
+%TVNET is a media company that controls several media portals.
 The most active accounts that use their application are \sn{TVnet\_portals}, \sn{RusApollo}, \sn{TVnet\_rus}, \sn{SportsTVNET}, and \sn{SejasLV}.
 
-The tweet delivery service \texttt{dlvr.it} is used by the newspaper \sn{nralv} and their sport portal \sn{Sportacentrs}, the photo account of the national news agency (LETA) \sn{letafoto}, \sn{Kompresori} and the sport account of Latvian Television \sn{ltvsports}.
+%The tweet delivery service \texttt{dlvr.it} is used by the newspaper \sn{nralv} and their sport portal \sn{Sportacentrs}, the photo account of the national news agency (LETA) \sn{letafoto}, \sn{Kompresori} and the sport account of Latvian Television \sn{ltvsports}.
 
-SKATIES delivers video content from several sources. The most active accounts are \sn{skatieslatvija}, \sn{lnt\_lv}, \sn{tv3lv}, \sn{BezTabuTV3} and \sn{TV3Zinas}.
+%SKATIES delivers video content from several sources. The most active accounts are \sn{skatieslatvija}, \sn{lnt\_lv}, \sn{tv3lv}, \sn{BezTabuTV3} and \sn{TV3Zinas}.
 
@@
 The top 5 most active users are: \sn{mixnews\_lv}, the Russian edition of a media portal, \sn{Otkrito}, also the Russian edition of \sn{JaunsLV}, \sn{labdienlv}, \sn{ekonimikalv} and \sn{nozare}, all three belonging to one Latvian media portal.
-The fact that Russian accounts are not active among other clients might suggest that Russian content is not spread via Twitter, but via Facebook.
+The fact that Russian accounts are not active among other clients might suggest that Russian content is not spread initially via Twitter, but is cross-posted from Facebook.
 % IMS but you said you were tracking Facebook.  I think you mean that you can only track FB when the content is also posted to Twitter, but not otherwise.
@@
 
-Latvian is the dominant language: \hl{880\,351 (74\%)} tweets are written in it.\footnotemark{} There are \hl{12\,505 (11\%)} tweets in Russian, \hl{116203 (10\%)} in English and \hl{66\,969 (6\%)} in other languages.
+Latvian is the dominant language: \hl{917\,259 (73.8\%)} tweets are written in it.\footnotemark{} There are \hl{130\,825 (10.5\%)} tweets in Russian, \hl{122\,490 (9.9\%)} in English and \hl{72\,369\, (6.2\%)} in other languages.
+This distribution is very different from a geo-located method used in \cite{milajevs:2017:BUCC}, where the distribution is 44.5\% Latvian, 33.9\% Russian and 20.7\% English.
 Figure~\ref{fig:rehydrated-tweets-count-by-day} shows the tweet volume over time.
@@
 Latvian dominates almost in every client application.
-Tweets coming from Foursquare are labeled as Latvian in \hl{78\%} cases (see Table~\ref{tab:source_counts}), that might be due to Latvian location names.
+Tweets coming from Foursquare are labeled as Latvian in \hl{78.4\%} cases (see Table~\ref{tab:source_counts}), that might be due to Latvian location names.
 
-Russian tweets constitute of more then half tweets coming from TVNET, where its share is \hl{52\%} while Latvian is \hl{46.3\%}, and from Facebook, where the two most active users are Russian madia.
+Russian tweets constitute of more then half tweets coming from TVNET, where its share is \hl{52.8\%} while Latvian is \hl{46.1\%}, and from Facebook, where the two most active users are Russian media.
 
-A lot of English content is coming form Instagram (\hl{32.9\%}), that might be due to the dominance of hashtags over other text.
+A lot of English content is coming form Instagram (\hl{36.1\%}), that might be due to the dominance of hashtags over other text.
 Also, there are many tweets labeled as written in other languages that come from Foursquare and Instagram.
@@
 \item \texttt{LV001: Winter} Everything about winter.
-\item \texttt{LV002: Mel\=anijas hronika} Mel\=anijas hronika is a Latvian movie that was selected for Foreign-Language Category for Oscars.
+\item \texttt{LV002: 
+The Chronicles of Melanie} Mel\=anijas hronika (The Chronicles of Melanie) is a Latvian movie that was selected for Foreign-Language Category for Oscars.
 \item \texttt{LV003: Refugees} A broad topic about refugee crisis in Europe, attitude to immigration and immigrants.
-\item \texttt{LV004: Dv\=eese\c{l}u putenis} A Latvian movie that is currently in production.
+\item \texttt{LV004: Blizzard of Souls} A Latvian movie Dv\=eese\c{l}u putenis (Blizzard of Souls) that is currently in production.
 \item \texttt{LV005: Ice hockey} Ice hockey related tweets.
@@
 Tweets in Latvian peak during Advent and Christmas in December, tweets in Russian reach maximum both in December and early January when Orthodox Christmas are celebrated.
-It worth noting that during the discussion whether Orthodox Christmas should be a public holiday, it sometimes was referred as ``Russian Christmas''.
+It worth noting that during the discussion whether Orthodox Christmas should be a public holiday, it sometimes was referred as ``Russian Christmas.''
 
@@
 This paper presents a multilingual tweet collection with some analysis of users, language use and content.
-The analysis reveal that the resource might be used in several areas ranging from computational linguistics, information retrieval and social science.
-
-As for computational linguistics, multilingual language identification needs to be applied to it, as tweets are not always monolingual, as we indirectly showed by the large volume of English tweets coming from Instagram and Latvian tweets coming from Foursquare.
-
-An evidence of the existence of reliable topics that exhibit various temporal patterns could be exploited in information retrieval either for evaluation of multilingual retrieval systems or development of collection exploration techniques.
-
-For social analysis, it would be nice to see what topics are multilingual, for example Winter, and what topics are monolingual, for example movie related topics in this work, and why the topics are discussed differently depending on a language.
+The analysis reveals that geo-location and a limited list of Twitter users leads to a biased collection.
+%
+% the resource might be used in several areas ranging from computational linguistics, information retrieval and social science.
+%
+The challenges of building representative and complete tweet collection are:
+\begin{itemize}
+\item How the content of users who do not engage with media accounts (newspapers, radio stations, etc.~\ldots) might be collected respecting their privacy and not introducing bias into the collection?
+\item How to get hints of what topics are more popular among ``minorities''? What are tweets in Russian and English are about?
+\item Some tweets are multilingual. How can code-switching be detected reliably?
+\end{itemize}
 

### 2018-05-17 paper.tex
Title
Intro

@@
 %\pretitle{Pretitle}
-\title{LV2}
-\runningtitle{LV2}
+\title{Language Bias in a Multilingual Tweet Corpus}
+%\runningtitle{LV2}
 %\subtitle{Subtitle}
@@
 %
-A tweet collection based on a curated list of users \cite{SANVICENTE16.465} is effective, but extra care must be taken as tracking personal accounts might be problematic due to privacy concerns.
+A tweet collection based on a curated list of users \cite{SANVICENTE16.465} is effective, but extra care must be taken as a thematic bias might be introduced.
 %
@@
 Such a collection would neither be biased linguistically because it is not based on a list of keywords, nor it would be biased thematically because it is not based on a list of users.
-However, a large number of tweets are not geo-located, which makes retrieval incomplete.
+The downside is that a large number of tweets are not geo-located, which makes retrieval incomplete.
 % IMS self-cite alert. What's new in this work?
@@
 %%%%%%%%
-To keep a balance between privacy and objectivity maximizing completeness, this work applies a hybrid approach by combining a geo-location based collection procedure with tracking a curated list of users.
-To minimize privacy issues, only accounts of organizations and public figures are tracked.
+To keep a balance between objectivity and completeness, this work applies a hybrid approach by combining a geo-location based collection procedure with tracking a curated list of users, which is based on the accounts of Latvian media outlets, politicians, government institutions and public figures.
 
 % IMS it's worth saying in one sentence how you will determine that the final collection has the properties you desire.
+Our base assumption is that geo-located tweets is a representative and unbiased sample of tweets from Latvia.
+Thus, an objective collection should exhibit similar properties as the geo-located one.
+The main property we study in this work is the language proportion.
+We hypothesize, that an objective extended collection should have similar language distribution as the initial.
 
-Our base assumption is that geo-located tweets is a representative and unbiased sample of Latvian Twitter.
-Thus, an extended collection should exhibit similar properties as the geo-located one.
-The main property we are interested in this work is the language proportion.
-We hypothesize, that an unbiased extended collection should have similar language distribution as the initial.
-
-To study the collection in more details, we defined 9 topics and manually search for relevant tweets.
+To study the collection in more details, we manually searched the collection for 9 topics of interest, so we could see whether topics introduce bias.
 
@@
 
-The analysis of the collection shows that it is biased toward content in Latvian: proportionally there are more tweets in Latvian than in Russian and English.
-Also, Latvian is more dominant language than expected in all but one topic, the exception being the topic about New Year celebration.
+The analysis shows that---despite our attempt---the extended collection is biased toward content in Latvian: proportionally there is more tweets in Latvian in the extended collection than in geo-located.
+We observe this phenomena not only in the extended collection, but also at the topical level.
+In all but one topic, Latvian is more dominant than expected.
 
@@
 Building an unbiased collection is difficult.
-In our case the main reason of introduced bias, might be that Russian and English content is less news-oriented and much more informal.
-In other words, while it's common to discuss current news in Latvian by engaging with media, the tweets in Russian and English might be more personal and friend-oriented.
+In our case the main reason of the introduced bias, might be that Russian and English content is less news-oriented and much more informal.
+In other words, while it is common to discuss current news in Latvian by engaging with the media, tweets in Russian and English tend to be personal and friend-oriented.
 

### 2018-05-17 paper.tex
Updates from ShareLaTeX

--- 2018-05-11 paper.tex
@@
 
-Our base assumption is that geo-located tweets is a representative and unbiased sample of Latvian Twitter.
+Our base assumption is that geo-located tweets are a representative and unbiased sample of Latvian Twitter.
 Thus, an extended collection should exhibit similar properties as the geo-located one.
@@
 
-To study the collection in more details, we defined 9 topics and manually search for relevant tweets.
+To study the collection in more detail, we defined 9 topics and manually search for relevant tweets.
 
@@
 Also, Latvian is more dominant language than expected in all but one topic, the exception being the topic about New Year celebration.
+# IMS I feel like this paragraph is hard to understand because the notion of "topics" hasn't been really defined yet.
+Since this is the introduction, the solution might be to make this statement more general.
 
@@
 In other words, while it's common to discuss current news in Latvian by engaging with media, the tweets in Russian and English might be more personal and friend-oriented.
+# IMS is this a hypothesis you intend to test here?  Or is this future work?  Or what?
 
@@
 %\footnotetext{The coordinates of the bounding box are \texttt{23.9325829, 56.8570671, 24.3247299, 57.0859184}.}
-%
+% IMS according to http://worldpopulationreview.com/countries/latvia-population/, the population of Riga is less than half the total population of Latvia.
+However, Twitter only allows bounding boxes for location to be so big, so you can't bound the whole country.
+
 In addition to the location, 420 accounts were tracked.%\footnotemark{} %\hl{The whole list of screen names together with user ID is available in the supplement.}

### 2018-05-17 paper.tex

--- 2018-05-17 paper.tex
@@
 % IMS it's worth saying in one sentence how you will determine that the final collection has the properties you desire.
-Our base assumption is that geo-located tweets is a representative and unbiased sample of tweets from Latvia.
+Our base assumption is that geo-located tweets are a representative and unbiased sample of tweets from Latvia.
 Thus, an objective collection should exhibit similar properties as the geo-located one.
@@
 
-To study the collection in more details, we manually searched the collection for 9 topics of interest, so we could see whether topics introduce bias.
+To study the collection in more detail, we manually searched the collection for 9 topics of interest, so we could see whether topics introduce bias.
 
@@
 The analysis shows that---despite our attempt---the extended collection is biased toward content in Latvian: proportionally there is more tweets in Latvian in the extended collection than in geo-located.
-We observe this phenomena not only in the extended collection, but also at the topical level.
+We observe this phenomena not only in the ``global level'' (the extended collection), but also at ``micro'' level (across the topics).
 In all but one topic, Latvian is more dominant than expected.
+% IMS I feel like this paragraph is hard to understand because the notion of "topics" hasn't been really defined yet.
+Since this is the introduction, the solution might be to make this statement more general.
 
@@
 In other words, while it is common to discuss current news in Latvian by engaging with the media, tweets in Russian and English tend to be personal and friend-oriented.
+% IMS is this a hypothesis you intend to test here?  Or is this future work?  Or what?
 

### 2018-05-17 paper.tex
Comments
Editing

@@
 %%%%%%%%%
-%There are several challenges of building a tweet collection that adequately represents language use in the country.
-%
 Building a monolingual Latvian collection could be done by harvesting tweets that contain indicative Latvian words which do not present in other languages, similarly to how it is done for Dutch \cite{sang2013}.
@@
 %
-%A geo-location based collection produces representative results \cite{milajevs:2017:BUCC}.
-%
 An alternative approach would be to retrieve only geo-located tweets.
@@
 The downside is that a large number of tweets are not geo-located, which makes retrieval incomplete.
-% IMS self-cite alert. What's new in this work?
 
@@
 
-% IMS it's worth saying in one sentence how you will determine that the final collection has the properties you desire.
 Our base assumption is that geo-located tweets are a representative and unbiased sample of tweets from Latvia.
@@
 The analysis shows that---despite our attempt---the extended collection is biased toward content in Latvian: proportionally there is more tweets in Latvian in the extended collection than in geo-located.
-We observe this phenomena not only in the ``global level'' (the extended collection), but also at ``micro'' level (across the topics).
+We observe this phenomena not only in the ``macro level'' (the whole collection), but also at ``micro level'' (across individual topics).
 In all but one topic, Latvian is more dominant than expected.
@@
 In other words, while it is common to discuss current news in Latvian by engaging with the media, tweets in Russian and English tend to be personal and friend-oriented.
+Future work should verify whether this is actually the case.
 % IMS is this a hypothesis you intend to test here?  Or is this future work?  Or what?
@@
 %
-The \texttt{locations} parameter was set to the bounding box of Riga, the capital of Latvia.%\footnotemark{}
+The \texttt{locations} parameter was set to the bounding box of Riga, the capital of Latvia.
+It is small enought to fit into Twitter API restrictions and covers about 40\% of the popilation of Latvia.%\footnotemark{}
 %
 %\footnotetext{The coordinates of the bounding box are \texttt{23.9325829, 56.8570671, 24.3247299, 57.0859184}.}
-% IMS according to http://worldpopulationreview.com/countries/latvia-population/, the population of Riga is less than half the total population of Latvia.
+% IMS.2 according to http://worldpopulationreview.com/countries/latvia-population/, the population of Riga is less than half the total population of Latvia.
 However, Twitter only allows bounding boxes for location to be so big, so you can't bound the whole country.
@@
 The content that comes from Foursquare and Instagram is created by the general public.
+% IMS.2 same comment as above... when you say "comes from" you mean crossposted content, right?  It's confusing because you also say "comes from" to mean the organization authoring the content.
 

### 2018-05-17 paper.tex
Comments

@@
 This paper presents a multilingual tweet collection with some analysis of users, language use and content.
-The analysis reveals that geo-location and a limited list of Twitter users leads to a biased collection.
-%
-% the resource might be used in several areas ranging from computational linguistics, information retrieval and social science.
-%
-The challenges of building representative and complete tweet collection are:
-\begin{itemize}
-\item How the content of users who do not engage with media accounts (newspapers, radio stations, etc.~\ldots) might be collected respecting their privacy and not introducing bias into the collection?
-\item How to get hints of what topics are more popular among ``minorities''? What are tweets in Russian and English are about?
-\item Some tweets are multilingual. How can code-switching be detected reliably?
-\end{itemize}
+The analysis revealed differences in language use between the geo-located collection, global collection and topical sub-collections.
+
+However, the question of whether the collection is any good remains open.
+It would be easy to test its extrinsic properties, for example, whether it leads to improvements in a language identification system when used as training data.
+But does not reveal its intrinsic properties.
+
+%The challenges of building representative and complete tweet collection are:
+%\begin{itemize}
+%\item How the content of users who do not engage with media accounts (newspapers, radio stations, etc.~\ldots) might be collected respecting their privacy and not introducing bias into the collection?
+%\item How to get hints of what topics are more popular among ``minorities''? What are tweets in Russian and English are about?
+%\item Some tweets are multilingual. How can code-switching be detected reliably?
+%\end{itemize}
 

### 2018-06-20 paper.tex
Initial review comments

--- 2018-05-17 paper.tex
@@
 
-%\usepackage{soul}
-%\definecolor{hlcolor}{RGB}{255, 221, 163}
-%\sethlcolor{hlcolor}
-\newcommand{\hl}[1]{#1}
+\usepackage{soul}
+\definecolor{hlcolor}{RGB}{255, 221, 163}
+\sethlcolor{hlcolor}
+%\newcommand{\hl}[1]{#1}
 
@@
 This paper presents a multilingual, location-anchored corpus of tweets from Latvia.
-The main challenge of collecting a socially representative corpus from this country is that several languages are used there: Latvian, the main communication language, Russian, the language of the largest minority in Latvia, and English.
+The main challenge of collecting a socially representative corpus from this country is that several languages are used there: Latvian, the main communication language and the only official language in Latvia, Russian, the language of the largest minority in Latvia, and English.
 
@@
 %
-Building a monolingual Latvian collection could be done by harvesting tweets that contain indicative Latvian words which do not present in other languages, similarly to how it is done for Dutch \cite{sang2013}.
+Building a monolingual Latvian collection could be done by harvesting tweets that contain indicative Latvian words, which are not present in other languages, similarly to how it is done for Dutch \cite{sang2013}.
 However, such an approach is not suitable for tweets in Russian and English, as these languages are widely used outside of Latvia.
@@
 
-The analysis shows that---despite our attempt---the extended collection is biased toward content in Latvian: proportionally there is more tweets in Latvian in the extended collection than in geo-located.
+The analysis shows that---despite our attempt---the extended collection is biased toward content in Latvian: proportionally there are more tweets in Latvian in the extended collection than in geo-located.
 We observe this phenomena not only in the ``global level'' (the extended collection), but also at ``micro'' level (across the topics).
@@
 %
-The \texttt{locations} parameter was set to the bounding box of Riga, the capital of Latvia.%\footnotemark{}
+Following \cite{milajevs:2017:BUCC}, the \texttt{locations} parameter was set to the bounding box of Riga, the capital of Latvia.\footnotemark{}
 %
-%\footnotetext{The coordinates of the bounding box are \texttt{23.9325829, 56.8570671, 24.3247299, 57.0859184}.}
-% IMS according to http://worldpopulationreview.com/countries/latvia-population/, the population of Riga is less than half the total population of Latvia.
+\footnotetext{The coordinates of the bounding box are \texttt{23.9325829, 56.8570671, 24.3247299, 57.0859184}.}
+% IMS.2 according to http://worldpopulationreview.com/countries/latvia-population/, the population of Riga is less than half the total population of Latvia.
 However, Twitter only allows bounding boxes for location to be so big, so you can't bound the whole country.
@@
 
-Russian tweets constitute of more then half tweets coming from TVNET, where its share is \hl{52.8\%} while Latvian is \hl{46.1\%}, and from Facebook, where the two most active users are Russian media.
+More than half tweets that come from TVNET are in Russian.
+Its share is \hl{52.8\%} while Latvian's is \hl{46.1\%}.
+Same goes for tweets that come from Facebook, where the two most active users are the Russian edision of media portals (\sn{mixnews\_lv} and \sn{Otkrito})
+
+, where the two most active users are Russian media.
 
@@
 
-To investigate the collection further nine topics of interests were defined. The collection was manually searched using keywords to get relevant tweets. The topics are:
+To investigate the collection further, \hl{nine} topics of interests were defined. The collection was manually searched using keywords to get relevant tweets. The topics are:
 \begin{itemize}
@@
 \item \texttt{LV003: Refugees} A broad topic about refugee crisis in Europe, attitude to immigration and immigrants.
-\item \texttt{LV004: Blizzard of Souls} A Latvian movie Dv\=eese\c{l}u putenis (Blizzard of Souls) that is currently in production.
+\item \texttt{LV004: Blizzard of Souls} A Latvian movie Dv\=ese\c{l}u putenis (Blizzard of Souls) that is currently in production.
 \item \texttt{LV005: Ice hockey} Ice hockey related tweets.
@@
 Tweets in Latvian peak during Advent and Christmas in December, tweets in Russian reach maximum both in December and early January when Orthodox Christmas are celebrated.
-It worth noting that during the discussion whether Orthodox Christmas should be a public holiday, it sometimes was referred as ``Russian Christmas.''
+It is worth noting that during the discussion whether Orthodox Christmas should be a public holiday, it sometimes was referred as ``Russian Christmas.''
 
@@
 For all topics the share of Latvian tweets is higher than on average in the collection (Section~\ref{sec:language}).
-For Russian and English these numbers are generally lower than global average.
+For Russian and English these numbers are generally lower than the global average.
 

### 2018-06-20 paper.tex

@@
 In all but one topic, Latvian is more dominant than expected.
-% IMS I feel like this paragraph is hard to understand because the notion of "topics" hasn't been really defined yet.
-Since this is the introduction, the solution might be to make this statement more general.
 
@@
 %
-Following \cite{milajevs:2017:BUCC}, the \texttt{locations} parameter was set to the bounding box of Riga, the capital of Latvia.\footnotemark{}
+Following \cite{milajevs:2017:BUCC}, the \texttt{locations} parameter was set to the bounding box of Riga, the capital of Latvia.
+It is small enought to fit into Twitter API restrictions and covers about 40\% of the popilation of Latvia.%\footnotemark{}
 %

### 2018-06-21 paper.tex
Minor

@@
 
+\newcommand{\sfile}[1]{\texttt{#1}}
+
 \begin{document}
@@
 
-\author[A]{\fnms{Anonymous} \snm{Submission}%
-\thanks{Corresponding Author: Book Production Manager, IOS Press, Nieuwe Hemweg 6B,
-1013 BG Amsterdam, The Netherlands; E-mail:
-bookproduction@iospress.nl.}}
+\author[A]{\fnms{Dmitrijs} \snm{Milajevs}%
+  \thanks{Corresponding Author: Dmitrijs Milajevs, Guest Researcher,
+    100 Bureau Drive,
+    Gaithersburg, MD 20899, USA%
+    ;
+    E-mail: dmitrijs.milajevs@nist.gov.}}
 %\author[B]{\fnms{Second} \snm{Author}}
@@
 
-%\runningauthor{B.P. Manager et al.}
-\address[A]{Confidential Review Copy, Do Not Distribute}
+\runningauthor{D. Milajevs}
+\address[A]{Guest Researcher at National Institute of Standards and Technology, Maryland, USA}
 %\address[B]{Short Affiliation of Second Author and Third Author}
@@
 
-In addition to the location, 420 accounts were tracked.%\footnotemark{} %\hl{The whole list of screen names together with user ID is available in the supplement.}
-%\footnotetext{In this paper, by ``tracking users'', we mean that their user IDs where passed to the Twitter API to collect tweets that they created, or the tweets that are replies by other users to their tweets.
-Refer to \url{https://developer.twitter.com/en/docs/tweets/filter-realtime/guides/basic-stream-parameters\#follow} for a complete description.
+In addition to the location, 420 accounts were tracked.\footnotemark{} The accounts are mostly Latvian (that is, coming from Latvia, but not necessary produce content in Latvian) news outlets, politicians, businesses, artists and sport clubs.
+We avoided following personal accounts to respect their privacy.
+We also avoided bootstrapping the list, as it might have introduced accounts that originate outside of Latvia, for example, \sn{BBC}.
+The whole list of screen names together with user IDs is available in the supplement file \sfile{lv.cfg}.
+
+\footnotetext{In this paper, by \hl{``tracking users''}, we mean that their user IDs where passed to the Twitter API to collect tweets that they created, or the tweets that are replies by other users to their tweets.
+Refer to \href{https://developer.twitter.com/en/docs/tweets/filter-realtime/guides/basic-stream-parameters\#follow}{to the Twitter documentation} for a complete description.
 Keep in mind that this is different from the case when a user follows another user.}
-%
-The accounts are mostly Latvian (that is, coming from Latvia, but not necessary produce content in Latvian) news outlets, politicians, businesses, artists and sport clubs.
 
@@
 \item \texttt{LV002: 
-The Chronicles of Melanie} Mel\=anijas hronika (The Chronicles of Melanie) is a Latvian movie that was selected for Foreign-Language Category for Oscars.
+The Chronicles of Melanie} Mel\=anijas Hronika (The Chronicles of Melanie) is a Latvian movie that was selected for Foreign-Language Category for Oscars.
 \item \texttt{LV003: Refugees} A broad topic about refugee crisis in Europe, attitude to immigration and immigrants.
-\item \texttt{LV004: Blizzard of Souls} A Latvian movie Dv\=ese\c{l}u putenis (Blizzard of Souls) that is currently in production.
+\item \texttt{LV004: Blizzard of Souls} A Latvian movie Dv\=ese\c{l}u Putenis (Blizzard of Souls) that is currently in production.
 \item \texttt{LV005: Ice hockey} Ice hockey related tweets.

### 2018-06-25 paper.tex
Minor

@@
 
-\footnotetext{In this paper, by \hl{``tracking users''}, we mean that their user IDs where passed to the Twitter API to collect tweets that they created, or the tweets that are replies by other users to their tweets.
+\footnotetext{In this paper, by \hl{``tracking users''}, we mean that their user IDs where passed to the Twitter API to collect tweets that they created, retweets of those tweets, or the tweets that are replies by other users to their tweets.
 Refer to \href{https://developer.twitter.com/en/docs/tweets/filter-realtime/guides/basic-stream-parameters\#follow}{to the Twitter documentation} for a complete description.

### 2018-06-25 paper.tex
Cleanup

@@
 
-To study the collection in more detail, we manually searched the collection for 9 topics of interest, so we could see whether topics introduce bias.
+To study the collection in more detail, we manually searched the collection for \hl{9} topics of interest.
 
@@
 The analysis shows that---despite our attempt---the extended collection is biased toward content in Latvian: proportionally there are more tweets in Latvian in the extended collection than in geo-located.
-We observe this phenomena not only in the ``global level'' (the extended collection), but also at ``micro'' level (across the topics).
-In all but one topic, Latvian is more dominant than expected.
+We observe this phenomena not only at the ``global level'' (the whole collection), but also at the ``micro'' level (across the topics).
+\hl{In all but one topic, Latvian is more dominant than expected.}
 
@@
 The twitter web client is used by both the general public and media companies.
-The top 5 of most active accounts consists only of tracked Latvian media accounts: \sn{DienaLV}, a newspaper, \sn{LA\_lv}, another newspaper, \sn{JaunsLV}, a media portal, \sn{TV3\_Play}, a TV channel, and \sn{dblv}, a newspaper.
+The top 5 of most active accounts consists only of tracked Latvian media accounts: \sn{DienaLV} (a newspaper), \sn{LA\_lv} (another newspaper), \sn{JaunsLV} (a media portal), \sn{TV3\_Play} (a TV channel), and \sn{dblv} (a newspaper).
 
@@
 % IMS I don't understand the previous sentence
-%For the TweetDeck, TVNET Login, dlvr.it and SKATIES client applications the top 5 users are tracked media accounts that write dominantly in Latvian.
+For the TweetDeck, TVNET Login, dlvr.it and SKATIES client applications the top 5 users are tracked media accounts that write dominantly in Latvian.
 The exceptions are a business account \sn{Kompresori} that was not tracked and tweets in three languages: Latvian, Russian and English, \sn{RusApollo} and \sn{TVNET\_rus} who tweet identical content exclusively in Russian, and \sn{SejasLV}, an exclusively Latvian account writing about celebrities, which was not tracked.
@@
 
-%TweetDeck is used by \sn{DelfiLV}, a major media portal, \sn{LV\_Portals}, an account run by the official government gazette of the Republic of Latvia, \sn{lsmlv}, an account of a publicly funded radio and television organization (LSM), \sn{ltvzinas}, the news account of Latvian Television, \sn{RietumuRadio}, a radio station.
+TweetDeck is used by \sn{DelfiLV}, a major media portal, \sn{LV\_Portals}, an account run by the official government gazette of the Republic of Latvia, \sn{lsmlv}, an account of a publicly funded radio and television organization (LSM), \sn{ltvzinas}, the news account of Latvian Television, \sn{RietumuRadio}, a radio station.
 
-%TVNET is a media company that controls several media portals.
+TVNET is a media company that controls several media portals.
 The most active accounts that use their application are \sn{TVnet\_portals}, \sn{RusApollo}, \sn{TVnet\_rus}, \sn{SportsTVNET}, and \sn{SejasLV}.
+As mentioned above, \sn{RusApollo} and \sn{TVnet\_rus} post identical messages.
 
-%The tweet delivery service \texttt{dlvr.it} is used by the newspaper \sn{nralv} and their sport portal \sn{Sportacentrs}, the photo account of the national news agency (LETA) \sn{letafoto}, \sn{Kompresori} and the sport account of Latvian Television \sn{ltvsports}.
+The tweet delivery service \texttt{dlvr.it} is used by the newspaper \sn{nralv} and their sport portal \sn{Sportacentrs}, the photo account of the national news agency (LETA) \sn{letafoto}, \sn{Kompresori} and the sport account of Latvian Television \sn{ltvsports}.
 
-%SKATIES delivers video content from several sources. The most active accounts are \sn{skatieslatvija}, \sn{lnt\_lv}, \sn{tv3lv}, \sn{BezTabuTV3} and \sn{TV3Zinas}.
+SKATIES delivers video content from several sources. The most active accounts are \sn{skatieslatvija}, \sn{lnt\_lv}, \sn{tv3lv}, \sn{BezTabuTV3} and \sn{TV3Zinas}.
 
@@
 Facebook content mostly comes from tracked media accounts.
-The top 5 most active users are: \sn{mixnews\_lv}, the Russian edition of a media portal, \sn{Otkrito}, also the Russian edition of \sn{JaunsLV}, \sn{labdienlv}, \sn{ekonimikalv} and \sn{nozare}, all three belonging to one Latvian media portal.
-The fact that Russian accounts are not active among other clients might suggest that Russian content is not spread initially via Twitter, but is cross-posted from Facebook.
+The top 5 most active users are: \sn{mixnews\_lv} (the Russian edition of the Mixnews.lv media portal), \sn{Otkrito} (the Russian edition of \sn{JaunsLV}), \sn{labdienlv}, \sn{ekonimikalv} and \sn{nozare}, all three belonging to one Latvian media portal.
+%The fact that Russian accounts are not active among other clients might suggest that Russian content is not spread initially via Twitter, but is cross-posted from Facebook.
 % IMS but you said you were tracking Facebook.  I think you mean that you can only track FB when the content is also posted to Twitter, but not otherwise.
 
-The content that comes from Foursquare and Instagram is created by the general public.
+%The content that is crossposted from Foursquare and Instagram is created by the accounts that are not followed.
 % IMS.2 same comment as above... when you say "comes from" you mean crossposted content, right?  It's confusing because you also say "comes from" to mean the organization authoring the content.
 
-There is a clear pattern that mobile clients are used by personal accounts, while media companies set up a special solution to deliver tweets, probably, integrating it with their content delivery systems or simply using a web client from an office machine.
+%There is a clear pattern that mobile clients are used by personal accounts, while media companies set up a special solution to deliver tweets, probably, integrating it with their content delivery systems or simply using a web client from an office machine.
 
@@
 
-Latvian dominates almost in every client application.
-Tweets coming from Foursquare are labeled as Latvian in \hl{78.4\%} cases (see Table~\ref{tab:source_counts}), that might be due to Latvian location names.
-
-More than half tweets that come from TVNET are in Russian.
-Its share is \hl{52.8\%} while Latvian's is \hl{46.1\%}.
-Same goes for tweets that come from Facebook, where the two most active users are the Russian edision of media portals (\sn{mixnews\_lv} and \sn{Otkrito})
-
-, where the two most active users are Russian media.
-
-A lot of English content is coming form Instagram (\hl{36.1\%}), that might be due to the dominance of hashtags over other text.
+%Latvian dominates almost in every client application (see Table~\ref{tab:source_counts}).
+%Tweets coming from Foursquare are labeled as Latvian in \hl{78.4\%} cases.
+% , that might be due to Latvian location names.
+%
+%More than half tweets that come from TVNET are in Russian. Its share is \hl{52.8\%} while Latvian's is \hl{46.1\%}.
+%
+%Same goes for tweets that come from Facebook, where the two most active users are the Russian edision of media portals (\sn{mixnews\_lv} and \sn{Otkrito}).
+%
+%A lot of English content is coming form Instagram (\hl{36.1\%}), that might be due to the dominance of hashtags over other text.
 Also, there are many tweets labeled as written in other languages that come from Foursquare and Instagram.

### 2018-06-25 paper.tex
More topics

@@
 
-To study the collection in more detail, we manually searched the collection for \hl{9} topics of interest.
+To study the collection in more detail, we manually searched the collection for \hl{16} topics of interest.
 
@@
 
-To investigate the collection further, \hl{nine} topics of interests were defined. The collection was manually searched using keywords to get relevant tweets. The topics are:
+To investigate the collection further, \hl{16} topics of interests were defined. The collection was manually searched using keywords to get relevant tweets. The topics are:
 \begin{itemize}
-\item \texttt{LV001: Winter} Everything about winter.
-\item \texttt{LV002: 
-The Chronicles of Melanie} Mel\=anijas Hronika (The Chronicles of Melanie) is a Latvian movie that was selected for Foreign-Language Category for Oscars.
-\item \texttt{LV003: Refugees} A broad topic about refugee crisis in Europe, attitude to immigration and immigrants.
-\item \texttt{LV004: Blizzard of Souls} A Latvian movie Dv\=ese\c{l}u Putenis (Blizzard of Souls) that is currently in production.
-\item \texttt{LV005: Ice hockey} Ice hockey related tweets.
-\item \texttt{LV006: Christmas} Christmas.
-\item \texttt{LV007: New Year} New Year.
-\item \texttt{LV008: Olympics} Tweets about the Olympic games and the Latvian team.
-\item \texttt{LV009: Brexit} Brexit.
+\item \texttt{LV016:} \textbf{Latvia 100} \ The Centennial Celebration of the Republic of Latvia.
+\item \texttt{LV005:} \textbf{Ice hockey} \ Ice hockey.
+\item \texttt{LV003:} \textbf{Refugees} \ Refugee crisis in Europe, attitude to immigration and immigrants.
+\item \texttt{LV009:} \textbf{Brexit} \ Withdrawal of the United Kingdom from the European Union known as Brexit.
+\item \texttt{LV001:} \textbf{Winter} \ Winter, snow and cold weather.
+\item \texttt{LV015:} \textbf{May 4} \ The Restoration of Independence Day.
+\item \texttt{LV011:} \textbf{May 8-9} \ Remembrance of the end of Word War II (May 8).
+It is also honored as the Victory Day on May 9.
+The Europe Day is observed on May 9.
+Tweets about any of the three events are relevant.
+\item \texttt{LV010:} \textbf{Midsummer} \ Midsummer celebration on June 23-24.
+\item \texttt{LV014:} \textbf{November 11} \ A memorial day for soldiers who fought for the independence of Latvia.
+\item \texttt{LV013:} \textbf{November 18} \ Proclamation Day of the Republic of Latvia.
+\item \texttt{LV006:} \textbf{Christmas} \ Christmas.
+\item \texttt{LV007:} \textbf{New Year} \ New Year.
+\item \texttt{LV008:} \textbf{Olympics} \ The Olympic games and the Latvian team.
+\item \texttt{LV002:} \textbf{The Chronicles of Melanie} \ Mel\=anijas Hronika (The Chronicles of Melanie) is a Latvian movie that was selected for the Foreign-Language Category for Oscars.
+\item \texttt{LV004:} \textbf{Blizzard of Souls} \ A Latvian movie Dv\=ese\c{l}u Putenis (Blizzard of Souls) that is in production by the time of writing.
 \end{itemize}

### 2018-06-25 paper.tex
Minor

@@
 %
-For the same reason, a TREC-like collection building approach \cite{lin2016overview} of filtering the publicly available stream of tweets by language would not work.
+For the same reason, a TREC-like collection building approach \cite{lin2017rts} of filtering the publicly available stream of tweets by language would not work.
 %
@@
 %%%%%%%%
-To keep a balance between objectivity and completeness, this work applies a hybrid approach by combining a geo-location based collection procedure with tracking a curated list of users, which is based on the accounts of Latvian media outlets, politicians, government institutions and public figures.
+To keep a balance between objectivity and completeness, this work applies a hybrid approach by combining a geo-location based collection procedure with following a curated list of users, which is based on the accounts of Latvian media outlets, politicians, government institutions and public figures.
 
@@
 
-In addition to the location, 420 accounts were tracked.\footnotemark{} The accounts are mostly Latvian (that is, coming from Latvia, but not necessary produce content in Latvian) news outlets, politicians, businesses, artists and sport clubs.
+In addition to the location, 420 accounts were followed.\footnotemark{} The accounts are mostly Latvian (that is, coming from Latvia, but not necessary produce content in Latvian) news outlets, politicians, businesses, artists and sport clubs.
 We avoided following personal accounts to respect their privacy.
@@
 
-\footnotetext{In this paper, by \hl{``tracking users''}, we mean that their user IDs where passed to the Twitter API to collect tweets that they created, retweets of those tweets, or the tweets that are replies by other users to their tweets.
+\footnotetext{In this paper, by ``following users'', we mean that their user IDs where passed to the Twitter API to collect tweets that they created, retweets of those tweets, or the tweets that are replies by other users to their tweets.
 Refer to \href{https://developer.twitter.com/en/docs/tweets/filter-realtime/guides/basic-stream-parameters\#follow}{to the Twitter documentation} for a complete description.
@@
 
-%To comply with Twitter's terms of service, on \hl{8 May 2018}, the raw tweet data was redownloaded to get rid of deleted tweets.
+To comply with Twitter's terms of service, on \hl{8 May 2018}, the raw tweet data was redownloaded to get rid of deleted tweets.
 The tweets that originated a retweet were added to the collection.
@@
 This resulted in \hl{1\,242\,943} tweets that formed the final collection presented here.
-% IMS I think "hydrate" is a jargon term that twarc invented but that isn't widely used.
 
@@
 The twitter web client is used by both the general public and media companies.
-The top 5 of most active accounts consists only of tracked Latvian media accounts: \sn{DienaLV} (a newspaper), \sn{LA\_lv} (another newspaper), \sn{JaunsLV} (a media portal), \sn{TV3\_Play} (a TV channel), and \sn{dblv} (a newspaper).
+The top 5 of most active accounts consists only of followed Latvian media accounts: \sn{DienaLV} (a newspaper), \sn{LA\_lv} (another newspaper), \sn{JaunsLV} (a media portal), \sn{TV3\_Play} (a TV channel), and \sn{dblv} (a newspaper).
 
-Notably, for mobile clients, the majority of tweets comes from the general public, because they are either geo-located or mention a tracked account.
-The number of tweets coming from tracked accounts, that are mostly media, is lower for Android \hl{(8.4\%)} than for iPhone \hl{(13.8\%)}.
-The difference can be explained by the fact, that all top 5 Android users are personal accounts, while for iPhone there are only 2 personal accounts in the top 5.
-\sn{TV3zinas}, a news account of a TV channel, tweets the most from iPhone.
-\sn{Lattelecom}, a telecommunication company, is the second most active iPhone user.
+%Notably, for mobile clients, the majority of tweets comes from \hl{the general public}, because they are either geo-located or mention a followed account.
+The proportion of tweets coming from followed accounts is lower for Android \hl{(8.4\%)} than for iPhone \hl{(13.8\%)}.
+The difference can be explained by the insight, that all top 5 Android users are personal accounts, while for iPhone there are only 2 personal accounts in the top 5.
+\sn{TV3zinas} (a news account of a TV channel) tweets the most from iPhone.
+\sn{Lattelecom} (a telecommunication company) is the second most active iPhone user.
 \sn{AstrologiLv} writes about astrology and is the fourth most active iPhone user.
-All three accounts tweet exclusively in Latvian and were tracked during corpus collection.
+All three accounts tweet exclusively in Latvian and were followed during corpus collection.
 
@@
 % IMS I don't understand the previous sentence
-For the TweetDeck, TVNET Login, dlvr.it and SKATIES client applications the top 5 users are tracked media accounts that write dominantly in Latvian.
-The exceptions are a business account \sn{Kompresori} that was not tracked and tweets in three languages: Latvian, Russian and English, \sn{RusApollo} and \sn{TVNET\_rus} who tweet identical content exclusively in Russian, and \sn{SejasLV}, an exclusively Latvian account writing about celebrities, which was not tracked.
+For the TweetDeck, TVNET Login, dlvr.it and SKATIES client applications the top 5 users are followed media accounts that write dominantly in Latvian.
+The exceptions are a business account \sn{Kompresori} that was not followed and tweets in three languages: Latvian, Russian and English, \sn{RusApollo} and \sn{TVNET\_rus} who tweet identical content exclusively in Russian, and \sn{SejasLV}, an exclusively Latvian account writing about celebrities, which was not followed.
 
@@
 
-TweetDeck is used by \sn{DelfiLV}, a major media portal, \sn{LV\_Portals}, an account run by the official government gazette of the Republic of Latvia, \sn{lsmlv}, an account of a publicly funded radio and television organization (LSM), \sn{ltvzinas}, the news account of Latvian Television, \sn{RietumuRadio}, a radio station.
+TweetDeck is used by \sn{DelfiLV} (a major media portal), \sn{LV\_Portals}, (the official government gazette), \sn{lsmlv} (a publicly funded radio and television organization (LSM)), \sn{ltvzinas} (the news account of Latvian Television) \sn{RietumuRadio} (a radio station).
 
@@
 
-Some tweets come from social media networks.
-Facebook content mostly comes from tracked media accounts.
-The top 5 most active users are: \sn{mixnews\_lv} (the Russian edition of the Mixnews.lv media portal), \sn{Otkrito} (the Russian edition of \sn{JaunsLV}), \sn{labdienlv}, \sn{ekonimikalv} and \sn{nozare}, all three belonging to one Latvian media portal.
+Some tweets are crossposts from other social media networks.
+Facebook content mostly comes from the followed media accounts.
+The top 5 most active users are: \sn{mixnews\_lv} (the Russian edition of the Mixnews.lv media portal), \sn{Otkrito} (the Russian edition of \sn{JaunsLV}), \sn{labdienlv}, \sn{ekonimikalv} and \sn{nozare} (all three belong to the same media company and tweet in Latvian).
 %The fact that Russian accounts are not active among other clients might suggest that Russian content is not spread initially via Twitter, but is cross-posted from Facebook.
@@
 \item \texttt{LV009:} \textbf{Brexit} \ Withdrawal of the United Kingdom from the European Union known as Brexit.
+\item \texttt{LV002:} \textbf{The Chronicles of Melanie} \ Mel\=anijas Hronika (The Chronicles of Melanie) is a Latvian movie that was selected for the Foreign-Language Category for Oscars.
+\item \texttt{LV004:} \textbf{Blizzard of Souls} \ A Latvian movie Dv\=ese\c{l}u Putenis (Blizzard of Souls) that is in production by the time of writing.
 \item \texttt{LV001:} \textbf{Winter} \ Winter, snow and cold weather.
@@
 \item \texttt{LV008:} \textbf{Olympics} \ The Olympic games and the Latvian team.
-\item \texttt{LV002:} \textbf{The Chronicles of Melanie} \ Mel\=anijas Hronika (The Chronicles of Melanie) is a Latvian movie that was selected for the Foreign-Language Category for Oscars.
-\item \texttt{LV004:} \textbf{Blizzard of Souls} \ A Latvian movie Dv\=ese\c{l}u Putenis (Blizzard of Souls) that is in production by the time of writing.
 \end{itemize}

### 2018-06-26 paper.tex
More changes

@@
 \usepackage{color}
-\usepackage[pdfusetitle]{hyperref}
+\usepackage{hyperref}
 % http://colorschemedesigner.com/#4o42FfqublRMS
@@
 }
+\def\UrlBreaks{\do\/\do-}
 
@@
 
+\hypersetup{pdfauthor={Dmitrijs Milajevs}}
 \author[A]{\fnms{Dmitrijs} \snm{Milajevs}%
@@
 %
-A tweet collection based on a curated list of users \cite{SANVICENTE16.465} is effective, but extra care must be taken as a thematic bias might be introduced.
+A tweet collection based on a curated list of users \cite{SANVICENTE16.465,L14-1642} is effective, but extra care must be taken as a thematic bias might be introduced.
 %
-An alternative approach would be to retrieve only geo-located tweets.
+An alternative approach would be to retrieve only geo-located tweets \cite{milajevs:2017:BUCC}.
 Such a collection would neither be biased linguistically because it is not based on a list of keywords, nor it would be biased thematically because it is not based on a list of users.
@@
 
-Over the period from 15 April 2017 to \hl{8 May 2018} the initial set of \hl{1\,708\,236} tweets was collected from the \texttt{POST status/filter} endpoint of the Twitter Streaming API.%\footnotemark{}
-%
-%\footnotetext{\url{https://developer.twitter.com/en/docs/tweets/filter-realtime/api-reference/post-statuses-filter}}
-%
+Over the period from 15 April 2017 to \hl{8 May 2018} the initial set of \hl{1\,708\,236} tweets was collected from the \texttt{POST status/filter} endpoint of the Twitter Streaming API.
 Following \cite{milajevs:2017:BUCC}, the \texttt{locations} parameter was set to the bounding box of Riga, the capital of Latvia.
@@
 \footnotetext{In this paper, by ``following users'', we mean that their user IDs where passed to the Twitter API to collect tweets that they created, retweets of those tweets, or the tweets that are replies by other users to their tweets.
-Refer to \href{https://developer.twitter.com/en/docs/tweets/filter-realtime/guides/basic-stream-parameters\#follow}{to the Twitter documentation} for a complete description.
+Refer to \href{https://developer.twitter.com/en/docs/tweets/filter-realtime/guides/basic-stream-parameters\#follow}{the Twitter documentation} for a complete description.
 Keep in mind that this is different from the case when a user follows another user.}
@@
 \item \texttt{LV008:} \textbf{Olympics} \ The Olympic games and the Latvian team.
+\item \texttt{LV012:} \textbf{March 16} \ Remembrance Day of the Latvian legionnaires.\footnotemark{}
 \end{itemize}
+
+\footnotetext{For more information about the event, refer to \url{http://www.mfa.gov.lv/en/policy/information-on-the-history-of-latvia/the-latvian-government-s-position-on-16-march-events}.}
 
@@
 During the Ice Hockey World Championship the volume of hockey related tweets increases.
-Similarly, event-based topics---such as Christmas, New Year and Olympics---are the most active during corresponding events, the volume of tweets slowly builds up as an event approaches.
+Similarly, event-based topics---such as Christmas, New Year and Olympics---are the most active during corresponding events, the volume of tweets builds up as an event approaches.
 
@@
 Table~\ref{tab:topic_lang_counts} shows the total number of tweets per topic and language share for Latvian, Russian and English.
-For all topics the share of Latvian tweets is higher than on average in the collection (Section~\ref{sec:language}).
+For most topics the share of Latvian tweets is higher than on average in the collection (Section~\ref{sec:language}).
 For Russian and English these numbers are generally lower than the global average.

### 2018-06-27 paper.tex
More references
Supplement files are links to Zenodo

@@
 
-\newcommand{\sfile}[1]{\texttt{#1}}
+\newcommand{\zenodoBase}{https://zenodo.org/record/1299195}
+\newcommand{\sfile}[1]{\href{\zenodoBase/files/#1}{#1}}
 
@@
 %
-An alternative approach would be to retrieve only geo-located tweets \cite{milajevs:2017:BUCC}.
+An alternative approach would be to retrieve only geo-located tweets \cite{coats_steven_2017,milajevs:2017:BUCC}.
 Such a collection would neither be biased linguistically because it is not based on a list of keywords, nor it would be biased thematically because it is not based on a list of users.
@@
 \footnotetext{In this paper, by ``following users'', we mean that their user IDs where passed to the Twitter API to collect tweets that they created, retweets of those tweets, or the tweets that are replies by other users to their tweets.
-Refer to \href{https://developer.twitter.com/en/docs/tweets/filter-realtime/guides/basic-stream-parameters\#follow}{the Twitter documentation} for a complete description.
+Refer to the \href{https://developer.twitter.com/en/docs/tweets/filter-realtime/guides/basic-stream-parameters\#follow}{Twitter documentation} for a complete description.
 Keep in mind that this is different from the case when a user follows another user.}
@@
 Also, we have noticed a large number of tweets that came from Sweden (probably because of the imprecise \texttt{locations} parameter value), so the tweets which location country code was \texttt{SE} were omitted.
-This resulted in \hl{1\,242\,943} tweets that formed the final collection presented here.
+This resulted in \hl{1\,242\,943} tweets that formed the final collection presented here.\footnotemark{}
+
+\footnotetext{The supplement files are available at Zenodo: \url{\zenodoBase}.
+Collected tweet IDs are available as \sfile{collected\_tweets.csv} and the final collection is available as \sfile{rehydrated\_tweets.csv}.
+The supplement files are licensed under a \href{https://creativecommons.org/publicdomain/zero/1.0/legalcode}{Creative Commons CCZero 1.0 License/Waiver}.}
 
@@
 
-To investigate the collection further, \hl{16} topics of interests were defined. The collection was manually searched using keywords to get relevant tweets. The topics are:
+To investigate the collection further, \hl{16} topics of interests were defined. The collection was manually searched using keywords to get relevant tweets. The topics are:\footnotemark{}
+\footnotetext{The topic file is available as \sfile{topics.json.txt}.}
 \begin{itemize}

### 2018-06-27 paper.tex
Stemming
Conclusion and future fork

@@
 \documentclass{IOS-Book-Article}
-
 \usepackage{graphicx}
@@
 
-To investigate the collection further, \hl{16} topics of interests were defined. The collection was manually searched using keywords to get relevant tweets. The topics are:\footnotemark{}
+To investigate the collection further, \hl{16} topics of interests were defined.
+The collection was manually searched using keywords to get relevant tweets.
+To compensate rich morphology in Latvian and Russian, keywords were manually stemmed.
+For example, \texttt{hokej} was used instead of Latvian \textit{hokejs} to search for the tweets about ice hockey.
+
+The topics are:\footnotemark{}
 \footnotetext{The topic file is available as \sfile{topics.json.txt}.}
@@
 How many topics should you have?
-Topics exhibit various temporal patterns, refer to Figure~\ref{fig:topic_timeline}. The volume of tweets is constant for long-lasting news stories such as the refugee crisis, Brexit and ice hockey.
+Topics exhibit various temporal patterns, refer to Figure~\ref{fig:topic_timeline}.
+The volume of tweets is constant for long-lasting news stories such as the centennial celebration, the refugee crisis, Brexit and ice hockey.
 %
@@
 Tweets in Latvian peak during Advent and Christmas in December, tweets in Russian reach maximum both in December and early January when Orthodox Christmas are celebrated.
-It is worth noting that during the discussion whether Orthodox Christmas should be a public holiday, it sometimes was referred as ``Russian Christmas.''
+It is worth noting that during the discussion whether Orthodox Christmas should be a public holiday, it sometimes was referred as ``Russian Christmas.'' In spring, November 11 became a public holiday, thus a spike in activity.
+Other event-related topics (May 4, May 8-9, etc.) behave similarly: their activity peaks during the event.
 
@@
 
-The most notable exception being Russian tweets about New Year, probably because of the content written by Russian tourists.
-The topic about Winter comes close for Russian with respect to the expected average, but is low for English tweets.
+The most notable exceptions (share of Russian tweets greater than \hl{10\%}) are Russian tweets about New Year and May 8-9.
+The topic about Winter comes close for Russian (\hl{9.6\%}) with respect to the expected average, but is low for English tweets.
 Interestingly, for the international news topics, there is proportionally more English content about Brexit than about refugees.
@@
 
-This paper presents a multilingual tweet collection with some analysis of users, language use and content.
+This paper presented a multilingual tweet collection with some analysis of users, language use and content.
 The analysis revealed differences in language use between the geo-located collection, global collection and topical sub-collections.
@@
 But does not reveal its intrinsic properties.
+However, we believe the presented dataset might be useful across different studies.
+
+As the corpus includes tweets of major media outlets and public figures, together with retweets and replies, it might be used to analyze public engagement.
+
+From the sociolinguistic perspective, instead of avoiding bias, one could study what linguistic environment the tweets represent.
+What are the factors determining the language, contents and stance of a tweet.
+How do these factors interact?
+Who are the people writing those tweets?
+
+Collection exploration trough keyword search showed that there is a lot of content on various topics and it should be feasible to run a shared retrieval task to evaluate retrieval systems and study what factors determine relevance.
 

### 2018-06-27 paper.tex
Merge

@@
 
+The tweets were written by \hl{41\,170} users.
+We refer to a user who produced at least 50 tweets as an \textit{active user}.
+There are \hl{2\,766} (\hl{6.7\%}) active users who produced \hl{1,196,558} (\hl{86.6\%}) tweets in total.
+
+Among active users, \hl{789} are monoligual. Exclusively in Latvian write \hl{631} (\hl{80.0\%}), in Russian \hl{40} (\hl{5.1\%}) and in English \hl{118} (\hl{15.0\%}).
+
 \footnotetext{Twitter labels tweets with the language they are written in.}

### 2018-06-27 paper.tex
Language uniformity

@@
 
+The Language uniformity score is defined in \cite{milajevs:2017:BUCC}.
+It is the normalized number of tweets in the most frequent language.
+Figure~\ref{fig:uniformity_score} compares the language uniformity scores of active users in this work and in \cite{milajevs:2017:BUCC}.
+Apart of the higher number of active users in this work (which is expected, as the corpus covers a longer period), the currently presented corpus has more active users with the language uniformity score about 0.5.
+Even though the majority is mostly monoligual, this work captured more (at least) bilingual users.
+
+\input{figures/uniformity_score.tex}
+
 \footnotetext{Twitter labels tweets with the language they are written in.}
@@
 \input{figures/topic_lang_counts.tex}
+\input{figures/topic_timeline.tex}
 
@@
 
-\input{figures/topic_timeline.tex}
-
 \bibliographystyle{unsrtnat}

### 2018-06-29 paper.tex
Aestetics
Topic titles
Minor

@@
 
+\input{figures/rehydrated_tweets_count_by_day.tex}
+
 Over the period from 15 April 2017 to \hl{8 May 2018} the initial set of \hl{1\,708\,236} tweets was collected from the \texttt{POST status/filter} endpoint of the Twitter Streaming API.
@@
 
-\input{figures/rehydrated_tweets_count_by_day.tex}
-
 Latvian is the dominant language: \hl{917\,259 (73.8\%)} tweets are written in it.\footnotemark{} There are \hl{130\,825 (10.5\%)} tweets in Russian, \hl{122\,490 (9.9\%)} in English and \hl{72\,369\, (6.2\%)} in other languages.
@@
 We refer to a user who produced at least 50 tweets as an \textit{active user}.
-There are \hl{2\,766} (\hl{6.7\%}) active users who produced \hl{1,196,558} (\hl{86.6\%}) tweets in total.
+There are \hl{2\,766} (\hl{6.7\%}) active users who produced \hl{1\,196\,558} (\hl{86.6\%}) tweets in total.
 
@@
 \item \texttt{LV016:} \textbf{Latvia 100} \ The Centennial Celebration of the Republic of Latvia.
-\item \texttt{LV005:} \textbf{Ice hockey} \ Ice hockey.
+\item \texttt{LV005:} \textbf{Ice Hockey} \ Ice hockey.
 \item \texttt{LV003:} \textbf{Refugees} \ Refugee crisis in Europe, attitude to immigration and immigrants.
@@
 Tweets in Latvian peak during Advent and Christmas in December, tweets in Russian reach maximum both in December and early January when Orthodox Christmas are celebrated.
-It is worth noting that during the discussion whether Orthodox Christmas should be a public holiday, it sometimes was referred as ``Russian Christmas.'' In spring, November 11 became a public holiday, thus a spike in activity.
+It is worth noting that during the discussion whether Orthodox Christmas should be a public holiday, it sometimes was referred as ``Russian Christmas.'' In spring 2018, there was a discussion to make November 11 a public holiday, thus a spike in activity.
 Other event-related topics (May 4, May 8-9, etc.) behave similarly: their activity peaks during the event.

### 2018-06-29 paper.tex
Topics

@@
 The analysis shows that---despite our attempt---the extended collection is biased toward content in Latvian: proportionally there are more tweets in Latvian in the extended collection than in geo-located.
-We observe this phenomena not only at the ``global level'' (the whole collection), but also at the ``micro'' level (across the topics).
+We observe this phenomena not only at the ``global level'' (the whole collection), but also at the ``micro level'' (across the topics).
 \hl{In all but one topic, Latvian is more dominant than expected.}
@@
 \begin{itemize}
-\item \texttt{LV016:} \textbf{Latvia 100} \ The Centennial Celebration of the Republic of Latvia.
-\item \texttt{LV005:} \textbf{Ice Hockey} \ Ice hockey.
+\item \texttt{LV001:} \textbf{Latvia 100} \ The Centennial Celebration of the Republic of Latvia.
+\item \texttt{LV002:} \textbf{Ice Hockey} \ Ice hockey.
 \item \texttt{LV003:} \textbf{Refugees} \ Refugee crisis in Europe, attitude to immigration and immigrants.
-\item \texttt{LV009:} \textbf{Brexit} \ Withdrawal of the United Kingdom from the European Union known as Brexit.
-\item \texttt{LV002:} \textbf{The Chronicles of Melanie} \ Mel\=anijas Hronika (The Chronicles of Melanie) is a Latvian movie that was selected for the Foreign-Language Category for Oscars.
-\item \texttt{LV004:} \textbf{Blizzard of Souls} \ A Latvian movie Dv\=ese\c{l}u Putenis (Blizzard of Souls) that is in production by the time of writing.
-\item \texttt{LV001:} \textbf{Winter} \ Winter, snow and cold weather.
-\item \texttt{LV015:} \textbf{May 4} \ The Restoration of Independence Day.
-\item \texttt{LV011:} \textbf{May 8-9} \ Remembrance of the end of Word War II (May 8).
+\item \texttt{LV004:} \textbf{Brexit} \ Withdrawal of the United Kingdom from the European Union known as Brexit.
+\item \texttt{LV005:} \textbf{Olympics} \ The Olympic games and the Latvian team.
+\item \texttt{LV006:} \textbf{Winter} \ Winter, snow and cold weather.
+\item \texttt{LV007:} \textbf{May 4} \ The Restoration of Independence Day.
+\item \texttt{LV008:} \textbf{May 8-9} \ Remembrance of the end of Word War II (May 8).
 It is also honored as the Victory Day on May 9.
@@
 Tweets about any of the three events are relevant.
-\item \texttt{LV010:} \textbf{Midsummer} \ Midsummer celebration on June 23-24.
-\item \texttt{LV014:} \textbf{November 11} \ A memorial day for soldiers who fought for the independence of Latvia.
-\item \texttt{LV013:} \textbf{November 18} \ Proclamation Day of the Republic of Latvia.
-\item \texttt{LV006:} \textbf{Christmas} \ Christmas.
-\item \texttt{LV007:} \textbf{New Year} \ New Year.
-\item \texttt{LV008:} \textbf{Olympics} \ The Olympic games and the Latvian team.
-\item \texttt{LV012:} \textbf{March 16} \ Remembrance Day of the Latvian legionnaires.\footnotemark{}
+\item \texttt{LV009:} \textbf{Midsummer} \ Midsummer celebration on June 23-24.
+\item \texttt{LV010:} \textbf{November 11} \ A memorial day for soldiers who fought for the independence of Latvia.
+\item \texttt{LV011:} \textbf{November 18} \ Proclamation Day of the Republic of Latvia.
+\item \texttt{LV012:} \textbf{Christmas} \ Christmas.
+\item \texttt{LV013:} \textbf{New Year} \ New Year.
+\item \texttt{LV014:} \textbf{March 16} \ Remembrance Day of the Latvian legionnaires.\footnotemark{}
+\item \texttt{LV015:} \textbf{The Chronicles of Melanie} \ Mel\=anijas Hronika (The Chronicles of Melanie) is a Latvian movie that was selected for the Foreign-Language Category for Oscars.
+\item \texttt{LV006:} \textbf{Blizzard of Souls} \ A Latvian movie Dv\=ese\c{l}u Putenis (Blizzard of Souls) that is in production by the time of writing.
 \end{itemize}

### 2018-07-17 paper.tex
Relevance judgments
Address

@@
 \author[A]{\fnms{Dmitrijs} \snm{Milajevs}%
-  \thanks{Corresponding Author: Dmitrijs Milajevs, Guest Researcher,
-    100 Bureau Drive,
-    Gaithersburg, MD 20899, USA%
-    ;
+  \thanks{Corresponding Author: Dmitrijs Milajevs
+    %, Guest Researcher,
+    %100 Bureau Drive,
+    %Gaithersburg, MD 20899, USA%
+    %;
     E-mail: dmitrijs.milajevs@nist.gov.}}
@@
 
-The topics are:\footnotemark{}
-\footnotetext{The topic file is available as \sfile{topics.json.txt}.}
+The topics are:\footnotemark{}%
+\footnotetext{The topic file is available as \sfile{topics.json.txt}. Relevance judgments are available as \sfile{relevance\_judgments.csv}.}%
 \begin{itemize}

### 2018-07-17 paper.tex
Text update

@@
 %\pretitle{Pretitle}
-\title{Language Bias in a Multilingual Tweet Corpus}
+\title{Language Use in a Multilingual Tweet Corpus}
 %\runningtitle{LV2}
@@
 
-%\begin{abstract}
-%
-%\end{abstract}
+\begin{abstract}
+A trilingual Latvian-Russian-English corpus of tweets is presented with an analysis of most users, language and topics.
+\end{abstract}
 
@@
 This paper presents a multilingual, location-anchored corpus of tweets from Latvia.
-The main challenge of collecting a socially representative corpus from this country is that several languages are used there: Latvian, the main communication language and the only official language in Latvia, Russian, the language of the largest minority in Latvia, and English.
+The main challenge of collecting a socially representative corpus from this country is that several languages are used there: Latvian, the main communication language and the only official language, Russian, the language of the largest minority, and English.
 
@@
 The main property we study in this work is the language proportion.
-We hypothesize, that an objective extended collection should have similar language distribution as the initial.
+We hypothesize, that an objectively extended collection should have similar language distribution as the initial.
 
@@
 The analysis shows that---despite our attempt---the extended collection is biased toward content in Latvian: proportionally there are more tweets in Latvian in the extended collection than in geo-located.
-We observe this phenomena not only at the ``global level'' (the whole collection), but also at the ``micro level'' (across the topics).
-\hl{In all but one topic, Latvian is more dominant than expected.}
+We observe this phenomena not only at the ``global level'' (the whole collection), but also at the ``local level'' (across the topics).
+\hl{In all topics, Latvian is more dominant than expected.}
 
@@
 
-Over the period from 15 April 2017 to \hl{8 May 2018} the initial set of \hl{1\,708\,236} tweets was collected from the \texttt{POST status/filter} endpoint of the Twitter Streaming API.
+Over the period from 15 April 2017 to \hl{16 July 2018} the initial set of \hl{1\,959\,695} tweets was collected from the \texttt{POST status/filter} endpoint of the Twitter Streaming API.
 Following \cite{milajevs:2017:BUCC}, the \texttt{locations} parameter was set to the bounding box of Riga, the capital of Latvia.
-It is small enought to fit into Twitter API restrictions and covers about 40\% of the popilation of Latvia.%\footnotemark{}
+It is small enought to fit into Twitter API restrictions and covers about 40\% of the popilation of Latvia.\footnotemark{}
 %
@@
 
-To comply with Twitter's terms of service, on \hl{8 May 2018}, the raw tweet data was redownloaded to get rid of deleted tweets.
+To comply with Twitter's terms of service, on \hl{16 July 2018}, the raw tweet data was redownloaded to get rid of deleted tweets.
 The tweets that originated a retweet were added to the collection.
 Also, we have noticed a large number of tweets that came from Sweden (probably because of the imprecise \texttt{locations} parameter value), so the tweets which location country code was \texttt{SE} were omitted.
-This resulted in \hl{1\,242\,943} tweets that formed the final collection presented here.\footnotemark{}
+This resulted in \hl{1\,415\,984} tweets that formed the final collection presented here.\footnotemark{}
 
@@
 
-On average, about \hl{3\,200} tweets were collected per day, which is more than 1\,500 by the geo-location based technique in \cite{milajevs:2017:BUCC}.
+On average, about \hl{3\,098} tweets were collected per day, which is more than 1\,500 by the geo-location based technique in \cite{milajevs:2017:BUCC}.
 Most of the tweets came from the official Twitter clients for Web, Android or iPhone.
@@
 
-The twitter web client is used by both the general public and media companies.
-The top 5 of most active accounts consists only of followed Latvian media accounts: \sn{DienaLV} (a newspaper), \sn{LA\_lv} (another newspaper), \sn{JaunsLV} (a media portal), \sn{TV3\_Play} (a TV channel), and \sn{dblv} (a newspaper).
+The top 5 of most active uses of the Twitter Web Client consists only of followed Latvian media accounts: \sn{DienaLV} (a newspaper), \sn{LA\_lv} (another newspaper), \sn{TV3\_Play} (a TV channel), \sn{JaunsLV} (a media portal), and \sn{dblv} (a newspaper).
 
 %Notably, for mobile clients, the majority of tweets comes from \hl{the general public}, because they are either geo-located or mention a followed account.
-The proportion of tweets coming from followed accounts is lower for Android \hl{(8.4\%)} than for iPhone \hl{(13.8\%)}.
-The difference can be explained by the insight, that all top 5 Android users are personal accounts, while for iPhone there are only 2 personal accounts in the top 5.
-\sn{TV3zinas} (a news account of a TV channel) tweets the most from iPhone.
-\sn{Lattelecom} (a telecommunication company) is the second most active iPhone user.
-\sn{AstrologiLv} writes about astrology and is the fourth most active iPhone user.
+%
+The proportion of tweets coming from followed accounts is lower for Android \hl{(8.5\%)} than for iPhone \hl{(14.6\%)}.
+All top 5 Android users are personal accounts, while for iPhone there are 2 personal accounts in the top 5.
+\sn{Lattelecom} (a telecommunication company) is the most active iPhone user. \sn{LRZinas} (a news account of Latvian Radio) is the second most active iPhone user.
+\sn{TV3zinas} (a news account of a TV channel) is the fifth most active iPhone user.
 All three accounts tweet exclusively in Latvian and were followed during corpus collection.
@@
 % IMS I don't understand the previous sentence
-For the TweetDeck, TVNET Login, dlvr.it and SKATIES client applications the top 5 users are followed media accounts that write dominantly in Latvian.
+For the TweetDeck, TVNET, dlvr.it and SKATIES client applications the top 5 users are followed media accounts that write dominantly in Latvian.
 The exceptions are a business account \sn{Kompresori} that was not followed and tweets in three languages: Latvian, Russian and English, \sn{RusApollo} and \sn{TVNET\_rus} who tweet identical content exclusively in Russian, and \sn{SejasLV}, an exclusively Latvian account writing about celebrities, which was not followed.
@@
 
-Latvian is the dominant language: \hl{917\,259 (73.8\%)} tweets are written in it.\footnotemark{} There are \hl{130\,825 (10.5\%)} tweets in Russian, \hl{122\,490 (9.9\%)} in English and \hl{72\,369\, (6.2\%)} in other languages.
+Latvian is the dominant language: \hl{1\,046\,412 (73.9\%)} tweets are written in it.\footnotemark{} There are \hl{149\,366 (10.5\%)} tweets in Russian, \hl{138\,492 (9.8\%)} in English and \hl{81\,714 (5.8\%)} in other languages.
 This distribution is very different from a geo-located method used in \cite{milajevs:2017:BUCC}, where the distribution is 44.5\% Latvian, 33.9\% Russian and 20.7\% English.
@@
 
-The tweets were written by \hl{41\,170} users.
+The tweets were written by \hl{41\,443} users.
 We refer to a user who produced at least 50 tweets as an \textit{active user}.
-There are \hl{2\,766} (\hl{6.7\%}) active users who produced \hl{1\,196\,558} (\hl{86.6\%}) tweets in total.
+There are \hl{2\,786} (\hl{6.7\%}) active users who produced \hl{1\,229\,010} (\hl{86.8\%}) tweets in total.
 
-Among active users, \hl{789} are monoligual. Exclusively in Latvian write \hl{631} (\hl{80.0\%}), in Russian \hl{40} (\hl{5.1\%}) and in English \hl{118} (\hl{15.0\%}).
+Among active users, \hl{797} are monoligual. Exclusively in Latvian write \hl{643} (\hl{80.7\%}), in Russian \hl{40} (\hl{5.0\%}) and in English \hl{114} (\hl{14.3\%}).
 
@@
 Table~\ref{tab:topic_lang_counts} shows the total number of tweets per topic and language share for Latvian, Russian and English.
-For most topics the share of Latvian tweets is higher than on average in the collection (Section~\ref{sec:language}).
+For \hl{all topics}, the share of Latvian tweets is higher than on average in the collection (Section~\ref{sec:language}).
 For Russian and English these numbers are generally lower than the global average.
+While for Russian only few topics are more active than expected, it is different for English, where some topics are twice more active than expected.
 
-The most notable exceptions (share of Russian tweets greater than \hl{10\%}) are Russian tweets about New Year and May 8-9.
-The topic about Winter comes close for Russian (\hl{9.6\%}) with respect to the expected average, but is low for English tweets.
-Interestingly, for the international news topics, there is proportionally more English content about Brexit than about refugees.
+The topics where share of Russian tweets is greater than \hl{9.8\%}New Year, May 8-9 and Winter. English most active topics are Latvia 100, May 4 and November 18, all of which are public celebrations.
 
@@
 But does not reveal its intrinsic properties.
-However, we believe the presented dataset might be useful across different studies.
+Nevertheless, we believe the presented dataset is useful across different studies.
 
@@
 
-From the sociolinguistic perspective, instead of avoiding bias, one could study what linguistic environment the tweets represent.
+From the sociolinguistic perspective, instead of avoiding collection artifacts such as collection bias, one could study what linguistic environment the tweets represent.
 What are the factors determining the language, contents and stance of a tweet.

### 2018-07-18 paper.tex
Update doi
New doi
Final details

@@
 
-\usepackage{soul}
-\definecolor{hlcolor}{RGB}{255, 221, 163}
-\sethlcolor{hlcolor}
-%\newcommand{\hl}[1]{#1}
+%\usepackage{soul}
+%\definecolor{hlcolor}{RGB}{255, 221, 163}
+%\sethlcolor{hlcolor}
+\newcommand{\hl}[1]{#1}
 
@@
 
-\newcommand{\zenodoBase}{https://zenodo.org/record/1299195}
+\newcommand{\zenodoBase}{https://zenodo.org/record/1313732}
 \newcommand{\sfile}[1]{\href{\zenodoBase/files/#1}{#1}}
@@
 \begin{abstract}
-A trilingual Latvian-Russian-English corpus of tweets is presented with an analysis of most users, language and topics.
+A trilingual Latvian-Russian-English corpus of tweets is presented with an analysis of users, language and topics.
+The corpus consists of 1.4 million tweets that cover a period from April 2017 to July 2018.
+The language analysis reveals that the majority of users mostly use one language.
+Across topics, there is more Latvian content than in the whole collection.
+Among many potential use cases, the corpus can be used, for example, to study the public engagement of major Latvian media outlets and public figures or the factors that determine language choice and content of a tweet.
 \end{abstract}
@@
 %
-A tweet collection based on a curated list of users \cite{SANVICENTE16.465,L14-1642} is effective, but extra care must be taken as a thematic bias might be introduced.
+A tweet collection based on a curated list of users \cite{SANVICENTE16.465,L14-1642} is effective, but extra care must be taken building the list of users.
 %
@@
 
-TweetDeck is used by \sn{DelfiLV} (a major media portal), \sn{LV\_Portals}, (the official government gazette), \sn{lsmlv} (a publicly funded radio and television organization (LSM)), \sn{ltvzinas} (the news account of Latvian Television) \sn{RietumuRadio} (a radio station).
+TweetDeck is used by \sn{DelfiLV} (a major media portal), \sn{LV\_Portals}, (the official government gazette), \sn{lsmlv} (a publicly funded radio and television organization, LSM), \sn{ltvzinas} (the news account of Latvian Television) \sn{RietumuRadio} (a radio station).
 
@@
 
-The Language uniformity score is defined in \cite{milajevs:2017:BUCC}.
-It is the normalized number of tweets in the most frequent language.
+The \textit{language uniformity score} is defined in \cite{milajevs:2017:BUCC}.
+It is the number of tweets in the most frequent language of a user normalized by the total number of tweets of that user.
 Figure~\ref{fig:uniformity_score} compares the language uniformity scores of active users in this work and in \cite{milajevs:2017:BUCC}.
@@
 For \hl{all topics}, the share of Latvian tweets is higher than on average in the collection (Section~\ref{sec:language}).
-For Russian and English these numbers are generally lower than the global average.
+
 While for Russian only few topics are more active than expected, it is different for English, where some topics are twice more active than expected.
-
-The topics where share of Russian tweets is greater than \hl{9.8\%}New Year, May 8-9 and Winter. English most active topics are Latvia 100, May 4 and November 18, all of which are public celebrations.
+The topics where share of Russian tweets is greater than expected \hl{9.8\%} are New Year, May 8-9 and Winter.
+English most active topics are Latvia 100, May 4 and November 18, all of which are public celebrations.
 
@@
 
-From the sociolinguistic perspective, instead of avoiding collection artifacts such as collection bias, one could study what linguistic environment the tweets represent.
+From the sociolinguistic perspective, instead of avoiding collection artifacts such as topical bias, one could study what linguistic environment the tweets represent.
 What are the factors determining the language, contents and stance of a tweet.
@@
 
-Collection exploration trough keyword search showed that there is a lot of content on various topics and it should be feasible to run a shared retrieval task to evaluate retrieval systems and study what factors determine relevance.
+Collection exploration trough keyword search showed that there is a lot of content on various topics and it should be feasible to run a shared retrieval task based on a multilingual collection from the Baltic region to evaluate retrieval systems and study what factors determine relevance.
 

### 2018-07-18 paper.tex
Updates from ShareLaTeX

--- 2018-07-17 paper.tex
@@
 \documentclass{IOS-Book-Article}
+
 \usepackage{graphicx}
@@
 \usepackage{color}
-\usepackage{hyperref}
+\usepackage[pdfusetitle]{hyperref}
 % http://colorschemedesigner.com/#4o42FfqublRMS
@@
 }
-\def\UrlBreaks{\do\/\do-}
 
-\usepackage{soul}
-\definecolor{hlcolor}{RGB}{255, 221, 163}
-\sethlcolor{hlcolor}
-%\newcommand{\hl}[1]{#1}
+%\usepackage{soul}
+%\definecolor{hlcolor}{RGB}{255, 221, 163}
+%\sethlcolor{hlcolor}
+\newcommand{\hl}[1]{#1}
 
@@
 
-\newcommand{\zenodoBase}{https://zenodo.org/record/1299195}
-\newcommand{\sfile}[1]{\href{\zenodoBase/files/#1}{#1}}
-
 \begin{document}
@@
 
-\hypersetup{pdfauthor={Dmitrijs Milajevs}}
-\author[A]{\fnms{Dmitrijs} \snm{Milajevs}%
-  \thanks{Corresponding Author: Dmitrijs Milajevs
-    %, Guest Researcher,
-    %100 Bureau Drive,
-    %Gaithersburg, MD 20899, USA%
-    %;
-    E-mail: dmitrijs.milajevs@nist.gov.}}
+\author[A]{\fnms{Anonymous} \snm{Submission}%
+\thanks{Corresponding Author: Book Production Manager, IOS Press, Nieuwe Hemweg 6B,
+1013 BG Amsterdam, The Netherlands; E-mail:
+bookproduction@iospress.nl.}}
 %\author[B]{\fnms{Second} \snm{Author}}
@@
 
-\runningauthor{D. Milajevs}
-\address[A]{Guest Researcher at National Institute of Standards and Technology, Maryland, USA}
+%\runningauthor{B.P. Manager et al.}
+\address[A]{Confidential Review Copy, Do Not Distribute}
 %\address[B]{Short Affiliation of Second Author and Third Author}
@@
 This paper presents a multilingual, location-anchored corpus of tweets from Latvia.
-The main challenge of collecting a socially representative corpus from this country is that several languages are used there: Latvian, the main communication language and the only official language in Latvia, Russian, the language of the largest minority in Latvia, and English.
+The main challenge of collecting a socially representative corpus from this country is that several languages are used there: Latvian, the main communication language, Russian, the language of the largest minority in Latvia, and English.
 
@@
 %%%%%%%%%
-%There are several challenges of building a tweet collection that adequately represents language use in the country.
-%
-Building a monolingual Latvian collection could be done by harvesting tweets that contain indicative Latvian words, which are not present in other languages, similarly to how it is done for Dutch \cite{sang2013}.
+Building a monolingual Latvian collection could be done by harvesting tweets that contain indicative Latvian words which do not present in other languages, similarly to how it is done for Dutch \cite{sang2013}.
 However, such an approach is not suitable for tweets in Russian and English, as these languages are widely used outside of Latvia.
 %
-For the same reason, a TREC-like collection building approach \cite{lin2017rts} of filtering the publicly available stream of tweets by language would not work.
+For the same reason, a TREC-like collection building approach \cite{lin2016overview} of filtering the publicly available stream of tweets by language would not work.
 %
-A tweet collection based on a curated list of users \cite{SANVICENTE16.465,L14-1642} is effective, but extra care must be taken as a thematic bias might be introduced.
+A tweet collection based on a curated list of users \cite{SANVICENTE16.465} is effective, but extra care must be taken as a thematic bias might be introduced.
 %
-An alternative approach would be to retrieve only geo-located tweets \cite{coats_steven_2017,milajevs:2017:BUCC}.
+An alternative approach would be to retrieve only geo-located tweets.
 Such a collection would neither be biased linguistically because it is not based on a list of keywords, nor it would be biased thematically because it is not based on a list of users.
@@
 %%%%%%%%
-To keep a balance between objectivity and completeness, this work applies a hybrid approach by combining a geo-location based collection procedure with following a curated list of users, which is based on the accounts of Latvian media outlets, politicians, government institutions and public figures.
+To keep a balance between objectivity and completeness, this work applies a hybrid approach by combining a geo-location based collection procedure with tracking a curated list of users, which is based on the accounts of Latvian media outlets, politicians, government institutions and public figures.
 
@@
 
-To study the collection in more detail, we manually searched the collection for \hl{16} topics of interest.
+To study the collection in more detail, we manually searched the collection for 9 topics of interest, so we could see whether topics introduce bias.
 
@@
 
-The analysis shows that---despite our attempt---the extended collection is biased toward content in Latvian: proportionally there are more tweets in Latvian in the extended collection than in geo-located.
-We observe this phenomena not only at the ``global level'' (the whole collection), but also at the ``micro level'' (across the topics).
-\hl{In all but one topic, Latvian is more dominant than expected.}
+The analysis shows that---despite our attempt---the extended collection is biased toward content in Latvian: proportionally there is more tweets in Latvian in the extended collection than in geo-located.
+We observe this phenomena not only in the ``macro level'' (the whole collection), but also at ``micro level'' (across individual topics).
+In all but one topic, Latvian is more dominant than expected.
+% IMS I feel like this paragraph is hard to understand because the notion of "topics" hasn't been really defined yet.
+Since this is the introduction, the solution might be to make this statement more general.
 
@@
 
-\input{figures/rehydrated_tweets_count_by_day.tex}
-
-Over the period from 15 April 2017 to \hl{8 May 2018} the initial set of \hl{1\,708\,236} tweets was collected from the \texttt{POST status/filter} endpoint of the Twitter Streaming API.
-Following \cite{milajevs:2017:BUCC}, the \texttt{locations} parameter was set to the bounding box of Riga, the capital of Latvia.
+Over the period from 15 April 2017 to \hl{8 May 2018} the initial set of \hl{1\,708\,236} tweets was collected from the \texttt{POST status/filter} endpoint of the Twitter Streaming API.%\footnotemark{}
+%
+%\footnotetext{\url{https://developer.twitter.com/en/docs/tweets/filter-realtime/api-reference/post-statuses-filter}}
+%
+The \texttt{locations} parameter was set to the bounding box of Riga, the capital of Latvia.
 It is small enought to fit into Twitter API restrictions and covers about 40\% of the popilation of Latvia.%\footnotemark{}
 %
-\footnotetext{The coordinates of the bounding box are \texttt{23.9325829, 56.8570671, 24.3247299, 57.0859184}.}
+%\footnotetext{The coordinates of the bounding box are \texttt{23.9325829, 56.8570671, 24.3247299, 57.0859184}.}
 % IMS.2 according to http://worldpopulationreview.com/countries/latvia-population/, the population of Riga is less than half the total population of Latvia.
@@
 
-In addition to the location, 420 accounts were followed.\footnotemark{} The accounts are mostly Latvian (that is, coming from Latvia, but not necessary produce content in Latvian) news outlets, politicians, businesses, artists and sport clubs.
-We avoided following personal accounts to respect their privacy.
-We also avoided bootstrapping the list, as it might have introduced accounts that originate outside of Latvia, for example, \sn{BBC}.
-The whole list of screen names together with user IDs is available in the supplement file \sfile{lv.cfg}.
-
-\footnotetext{In this paper, by ``following users'', we mean that their user IDs where passed to the Twitter API to collect tweets that they created, retweets of those tweets, or the tweets that are replies by other users to their tweets.
-Refer to the \href{https://developer.twitter.com/en/docs/tweets/filter-realtime/guides/basic-stream-parameters\#follow}{Twitter documentation} for a complete description.
+In addition to the location, 420 accounts were tracked.%\footnotemark{} %\hl{The whole list of screen names together with user ID is available in the supplement.}
+%\footnotetext{In this paper, by ``tracking users'', we mean that their user IDs where passed to the Twitter API to collect tweets that they created, or the tweets that are replies by other users to their tweets.
+Refer to \url{https://developer.twitter.com/en/docs/tweets/filter-realtime/guides/basic-stream-parameters\#follow} for a complete description.
 Keep in mind that this is different from the case when a user follows another user.}
+%
+The accounts are mostly Latvian (that is, coming from Latvia, but not necessary produce content in Latvian) news outlets, politicians, businesses, artists and sport clubs.
 
@@
 
-To comply with Twitter's terms of service, on \hl{8 May 2018}, the raw tweet data was redownloaded to get rid of deleted tweets.
+%To comply with Twitter's terms of service, on \hl{8 May 2018}, the raw tweet data was redownloaded to get rid of deleted tweets.
 The tweets that originated a retweet were added to the collection.
 Also, we have noticed a large number of tweets that came from Sweden (probably because of the imprecise \texttt{locations} parameter value), so the tweets which location country code was \texttt{SE} were omitted.
-This resulted in \hl{1\,242\,943} tweets that formed the final collection presented here.\footnotemark{}
-
-\footnotetext{The supplement files are available at Zenodo: \url{\zenodoBase}.
-Collected tweet IDs are available as \sfile{collected\_tweets.csv} and the final collection is available as \sfile{rehydrated\_tweets.csv}.
-The supplement files are licensed under a \href{https://creativecommons.org/publicdomain/zero/1.0/legalcode}{Creative Commons CCZero 1.0 License/Waiver}.}
+This resulted in \hl{1\,242\,943} tweets that formed the final collection presented here.
+% IMS I think "hydrate" is a jargon term that twarc invented but that isn't widely used.
 
@@
 The twitter web client is used by both the general public and media companies.
-The top 5 of most active accounts consists only of followed Latvian media accounts: \sn{DienaLV} (a newspaper), \sn{LA\_lv} (another newspaper), \sn{JaunsLV} (a media portal), \sn{TV3\_Play} (a TV channel), and \sn{dblv} (a newspaper).
+The top 5 of most active accounts consists only of tracked Latvian media accounts: \sn{DienaLV}, a newspaper, \sn{LA\_lv}, another newspaper, \sn{JaunsLV}, a media portal, \sn{TV3\_Play}, a TV channel, and \sn{dblv}, a newspaper.
 
-%Notably, for mobile clients, the majority of tweets comes from \hl{the general public}, because they are either geo-located or mention a followed account.
-The proportion of tweets coming from followed accounts is lower for Android \hl{(8.4\%)} than for iPhone \hl{(13.8\%)}.
-The difference can be explained by the insight, that all top 5 Android users are personal accounts, while for iPhone there are only 2 personal accounts in the top 5.
-\sn{TV3zinas} (a news account of a TV channel) tweets the most from iPhone.
-\sn{Lattelecom} (a telecommunication company) is the second most active iPhone user.
+Notably, for mobile clients, the majority of tweets comes from the general public, because they are either geo-located or mention a tracked account.
+The number of tweets coming from tracked accounts, that are mostly media, is lower for Android \hl{(8.4\%)} than for iPhone \hl{(13.8\%)}.
+The difference can be explained by the fact, that all top 5 Android users are personal accounts, while for iPhone there are only 2 personal accounts in the top 5.
+\sn{TV3zinas}, a news account of a TV channel, tweets the most from iPhone.
+\sn{Lattelecom}, a telecommunication company, is the second most active iPhone user.
 \sn{AstrologiLv} writes about astrology and is the fourth most active iPhone user.
-All three accounts tweet exclusively in Latvian and were followed during corpus collection.
+All three accounts tweet exclusively in Latvian and were tracked during corpus collection.
 
@@
 % IMS I don't understand the previous sentence
-For the TweetDeck, TVNET Login, dlvr.it and SKATIES client applications the top 5 users are followed media accounts that write dominantly in Latvian.
-The exceptions are a business account \sn{Kompresori} that was not followed and tweets in three languages: Latvian, Russian and English, \sn{RusApollo} and \sn{TVNET\_rus} who tweet identical content exclusively in Russian, and \sn{SejasLV}, an exclusively Latvian account writing about celebrities, which was not followed.
+%For the TweetDeck, TVNET Login, dlvr.it and SKATIES client applications the top 5 users are tracked media accounts that write dominantly in Latvian.
+The exceptions are a business account \sn{Kompresori} that was not tracked and tweets in three languages: Latvian, Russian and English, \sn{RusApollo} and \sn{TVNET\_rus} who tweet identical content exclusively in Russian, and \sn{SejasLV}, an exclusively Latvian account writing about celebrities, which was not tracked.
 
@@
 
-TweetDeck is used by \sn{DelfiLV} (a major media portal), \sn{LV\_Portals}, (the official government gazette), \sn{lsmlv} (a publicly funded radio and television organization (LSM)), \sn{ltvzinas} (the news account of Latvian Television) \sn{RietumuRadio} (a radio station).
+%TweetDeck is used by \sn{DelfiLV}, a major media portal, \sn{LV\_Portals}, an account run by the official government gazette of the Republic of Latvia, \sn{lsmlv}, an account of a publicly funded radio and television organization (LSM), \sn{ltvzinas}, the news account of Latvian Television, \sn{RietumuRadio}, a radio station.
 
-TVNET is a media company that controls several media portals.
+%TVNET is a media company that controls several media portals.
 The most active accounts that use their application are \sn{TVnet\_portals}, \sn{RusApollo}, \sn{TVnet\_rus}, \sn{SportsTVNET}, and \sn{SejasLV}.
-As mentioned above, \sn{RusApollo} and \sn{TVnet\_rus} post identical messages.
 
-The tweet delivery service \texttt{dlvr.it} is used by the newspaper \sn{nralv} and their sport portal \sn{Sportacentrs}, the photo account of the national news agency (LETA) \sn{letafoto}, \sn{Kompresori} and the sport account of Latvian Television \sn{ltvsports}.
+%The tweet delivery service \texttt{dlvr.it} is used by the newspaper \sn{nralv} and their sport portal \sn{Sportacentrs}, the photo account of the national news agency (LETA) \sn{letafoto}, \sn{Kompresori} and the sport account of Latvian Television \sn{ltvsports}.
 
-SKATIES delivers video content from several sources. The most active accounts are \sn{skatieslatvija}, \sn{lnt\_lv}, \sn{tv3lv}, \sn{BezTabuTV3} and \sn{TV3Zinas}.
+%SKATIES delivers video content from several sources. The most active accounts are \sn{skatieslatvija}, \sn{lnt\_lv}, \sn{tv3lv}, \sn{BezTabuTV3} and \sn{TV3Zinas}.
 
-Some tweets are crossposts from other social media networks.
-Facebook content mostly comes from the followed media accounts.
-The top 5 most active users are: \sn{mixnews\_lv} (the Russian edition of the Mixnews.lv media portal), \sn{Otkrito} (the Russian edition of \sn{JaunsLV}), \sn{labdienlv}, \sn{ekonimikalv} and \sn{nozare} (all three belong to the same media company and tweet in Latvian).
-%The fact that Russian accounts are not active among other clients might suggest that Russian content is not spread initially via Twitter, but is cross-posted from Facebook.
+Some tweets come from social media networks.
+Facebook content mostly comes from tracked media accounts.
+The top 5 most active users are: \sn{mixnews\_lv}, the Russian edition of a media portal, \sn{Otkrito}, also the Russian edition of \sn{JaunsLV}, \sn{labdienlv}, \sn{ekonimikalv} and \sn{nozare}, all three belonging to one Latvian media portal.
+The fact that Russian accounts are not active among other clients might suggest that Russian content is not spread initially via Twitter, but is cross-posted from Facebook.
 % IMS but you said you were tracking Facebook.  I think you mean that you can only track FB when the content is also posted to Twitter, but not otherwise.
 
-%The content that is crossposted from Foursquare and Instagram is created by the accounts that are not followed.
+The content that comes from Foursquare and Instagram is created by the general public.
 % IMS.2 same comment as above... when you say "comes from" you mean crossposted content, right?  It's confusing because you also say "comes from" to mean the organization authoring the content.
 
-%There is a clear pattern that mobile clients are used by personal accounts, while media companies set up a special solution to deliver tweets, probably, integrating it with their content delivery systems or simply using a web client from an office machine.
+There is a clear pattern that mobile clients are used by personal accounts, while media companies set up a special solution to deliver tweets, probably, integrating it with their content delivery systems or simply using a web client from an office machine.
 
@@
 
+\input{figures/rehydrated_tweets_count_by_day.tex}
+
 Latvian is the dominant language: \hl{917\,259 (73.8\%)} tweets are written in it.\footnotemark{} There are \hl{130\,825 (10.5\%)} tweets in Russian, \hl{122\,490 (9.9\%)} in English and \hl{72\,369\, (6.2\%)} in other languages.
@@
 
-The tweets were written by \hl{41\,170} users.
-We refer to a user who produced at least 50 tweets as an \textit{active user}.
-There are \hl{2\,766} (\hl{6.7\%}) active users who produced \hl{1\,196\,558} (\hl{86.6\%}) tweets in total.
-
-Among active users, \hl{789} are monoligual. Exclusively in Latvian write \hl{631} (\hl{80.0\%}), in Russian \hl{40} (\hl{5.1\%}) and in English \hl{118} (\hl{15.0\%}).
-
-The Language uniformity score is defined in \cite{milajevs:2017:BUCC}.
-It is the normalized number of tweets in the most frequent language.
-Figure~\ref{fig:uniformity_score} compares the language uniformity scores of active users in this work and in \cite{milajevs:2017:BUCC}.
-Apart of the higher number of active users in this work (which is expected, as the corpus covers a longer period), the currently presented corpus has more active users with the language uniformity score about 0.5.
-Even though the majority is mostly monoligual, this work captured more (at least) bilingual users.
-
-\input{figures/uniformity_score.tex}
-
 \footnotetext{Twitter labels tweets with the language they are written in.}
 
-%Latvian dominates almost in every client application (see Table~\ref{tab:source_counts}).
-%Tweets coming from Foursquare are labeled as Latvian in \hl{78.4\%} cases.
-% , that might be due to Latvian location names.
-%
-%More than half tweets that come from TVNET are in Russian. Its share is \hl{52.8\%} while Latvian's is \hl{46.1\%}.
-%
-%Same goes for tweets that come from Facebook, where the two most active users are the Russian edision of media portals (\sn{mixnews\_lv} and \sn{Otkrito}).
-%
-%A lot of English content is coming form Instagram (\hl{36.1\%}), that might be due to the dominance of hashtags over other text.
+Latvian dominates almost in every client application.
+Tweets coming from Foursquare are labeled as Latvian in \hl{78.4\%} cases (see Table~\ref{tab:source_counts}), that might be due to Latvian location names.
+
+Russian tweets constitute of more then half tweets coming from TVNET, where its share is \hl{52.8\%} while Latvian is \hl{46.1\%}, and from Facebook, where the two most active users are Russian media.
+
+A lot of English content is coming form Instagram (\hl{36.1\%}), that might be due to the dominance of hashtags over other text.
 Also, there are many tweets labeled as written in other languages that come from Foursquare and Instagram.
@@
 
-To investigate the collection further, \hl{16} topics of interests were defined.
-The collection was manually searched using keywords to get relevant tweets.
-To compensate rich morphology in Latvian and Russian, keywords were manually stemmed.
-For example, \texttt{hokej} was used instead of Latvian \textit{hokejs} to search for the tweets about ice hockey.
-
-The topics are:\footnotemark{}%
-\footnotetext{The topic file is available as \sfile{topics.json.txt}. Relevance judgments are available as \sfile{relevance\_judgments.csv}.}%
+To investigate the collection further nine topics of interests were defined. The collection was manually searched using keywords to get relevant tweets. The topics are:
 \begin{itemize}
-\item \texttt{LV001:} \textbf{Latvia 100} \ The Centennial Celebration of the Republic of Latvia.
-\item \texttt{LV002:} \textbf{Ice Hockey} \ Ice hockey.
-\item \texttt{LV003:} \textbf{Refugees} \ Refugee crisis in Europe, attitude to immigration and immigrants.
-\item \texttt{LV004:} \textbf{Brexit} \ Withdrawal of the United Kingdom from the European Union known as Brexit.
-\item \texttt{LV005:} \textbf{Olympics} \ The Olympic games and the Latvian team.
-\item \texttt{LV006:} \textbf{Winter} \ Winter, snow and cold weather.
-\item \texttt{LV007:} \textbf{May 4} \ The Restoration of Independence Day.
-\item \texttt{LV008:} \textbf{May 8-9} \ Remembrance of the end of Word War II (May 8).
-It is also honored as the Victory Day on May 9.
-The Europe Day is observed on May 9.
-Tweets about any of the three events are relevant.
-\item \texttt{LV009:} \textbf{Midsummer} \ Midsummer celebration on June 23-24.
-\item \texttt{LV010:} \textbf{November 11} \ A memorial day for soldiers who fought for the independence of Latvia.
-\item \texttt{LV011:} \textbf{November 18} \ Proclamation Day of the Republic of Latvia.
-\item \texttt{LV012:} \textbf{Christmas} \ Christmas.
-\item \texttt{LV013:} \textbf{New Year} \ New Year.
-\item \texttt{LV014:} \textbf{March 16} \ Remembrance Day of the Latvian legionnaires.\footnotemark{}
-\item \texttt{LV015:} \textbf{The Chronicles of Melanie} \ Mel\=anijas Hronika (The Chronicles of Melanie) is a Latvian movie that was selected for the Foreign-Language Category for Oscars.
-\item \texttt{LV006:} \textbf{Blizzard of Souls} \ A Latvian movie Dv\=ese\c{l}u Putenis (Blizzard of Souls) that is in production by the time of writing.
+\item \texttt{LV001: Winter} Everything about winter.
+\item \texttt{LV002: 
+The Chronicles of Melanie} Mel\=anijas hronika (The Chronicles of Melanie) is a Latvian movie that was selected for Foreign-Language Category for Oscars.
+\item \texttt{LV003: Refugees} A broad topic about refugee crisis in Europe, attitude to immigration and immigrants.
+\item \texttt{LV004: Blizzard of Souls} A Latvian movie Dv\=eese\c{l}u putenis (Blizzard of Souls) that is currently in production.
+\item \texttt{LV005: Ice hockey} Ice hockey related tweets.
+\item \texttt{LV006: Christmas} Christmas.
+\item \texttt{LV007: New Year} New Year.
+\item \texttt{LV008: Olympics} Tweets about the Olympic games and the Latvian team.
+\item \texttt{LV009: Brexit} Brexit.
 \end{itemize}
-
-\footnotetext{For more information about the event, refer to \url{http://www.mfa.gov.lv/en/policy/information-on-the-history-of-latvia/the-latvian-government-s-position-on-16-march-events}.}
 
@@
 How many topics should you have?
-Topics exhibit various temporal patterns, refer to Figure~\ref{fig:topic_timeline}.
-The volume of tweets is constant for long-lasting news stories such as the centennial celebration, the refugee crisis, Brexit and ice hockey.
+Topics exhibit various temporal patterns, refer to Figure~\ref{fig:topic_timeline}. The volume of tweets is constant for long-lasting news stories such as the refugee crisis, Brexit and ice hockey.
 %
 During the Ice Hockey World Championship the volume of hockey related tweets increases.
-Similarly, event-based topics---such as Christmas, New Year and Olympics---are the most active during corresponding events, the volume of tweets builds up as an event approaches.
+Similarly, event-based topics---such as Christmas, New Year and Olympics---are the most active during corresponding events, the volume of tweets slowly builds up as an event approaches.
 
@@
 Tweets in Latvian peak during Advent and Christmas in December, tweets in Russian reach maximum both in December and early January when Orthodox Christmas are celebrated.
-It is worth noting that during the discussion whether Orthodox Christmas should be a public holiday, it sometimes was referred as ``Russian Christmas.'' In spring 2018, there was a discussion to make November 11 a public holiday, thus a spike in activity.
-Other event-related topics (May 4, May 8-9, etc.) behave similarly: their activity peaks during the event.
+It worth noting that during the discussion whether Orthodox Christmas should be a public holiday, it sometimes was referred as ``Russian Christmas.''
 
@@
 Table~\ref{tab:topic_lang_counts} shows the total number of tweets per topic and language share for Latvian, Russian and English.
-For most topics the share of Latvian tweets is higher than on average in the collection (Section~\ref{sec:language}).
-For Russian and English these numbers are generally lower than the global average.
+For all topics the share of Latvian tweets is higher than on average in the collection (Section~\ref{sec:language}).
+For Russian and English these numbers are generally lower than global average.
 
-The most notable exceptions (share of Russian tweets greater than \hl{10\%}) are Russian tweets about New Year and May 8-9.
-The topic about Winter comes close for Russian (\hl{9.6\%}) with respect to the expected average, but is low for English tweets.
+The most notable exception being Russian tweets about New Year, probably because of the content written by Russian tourists.
+The topic about Winter comes close for Russian with respect to the expected average, but is low for English tweets.
 Interestingly, for the international news topics, there is proportionally more English content about Brexit than about refugees.
@@
 \input{figures/topic_lang_counts.tex}
-\input{figures/topic_timeline.tex}
 
@@
 
-This paper presented a multilingual tweet collection with some analysis of users, language use and content.
+This paper presents a multilingual tweet collection with some analysis of users, language use and content.
 The analysis revealed differences in language use between the geo-located collection, global collection and topical sub-collections.
@@
 But does not reveal its intrinsic properties.
-However, we believe the presented dataset might be useful across different studies.
 
-As the corpus includes tweets of major media outlets and public figures, together with retweets and replies, it might be used to analyze public engagement.
+Riga was chosen as the basis fro the geo-located collection, but the demographic in the city (larger proportion of ethinc Russians)  is different than in the rest of the country, especially its Western parts (larger proportion of ethnic Latvians).
+Taking this in the account, our global collection might be less biased that the geo-located one!
+However, it is an open question, whether geo-location of a larger area, for example, by tracking top 10 largest cities, improves the result.
 
-From the sociolinguistic perspective, instead of avoiding bias, one could study what linguistic environment the tweets represent.
-What are the factors determining the language, contents and stance of a tweet.
-How do these factors interact?
-Who are the people writing those tweets?
-
-Collection exploration trough keyword search showed that there is a lot of content on various topics and it should be feasible to run a shared retrieval task to evaluate retrieval systems and study what factors determine relevance.
+Is it possible to control for bias using the tools described here?
+If we tracked more accounts that tweet dominantly in English, would that introduce other biases?
+Is it possible to select a mixture of topics such that every language would have few topics it dominates?
+How these topics should be explored?
 
@@
 
+\input{figures/topic_timeline.tex}
+
 \bibliographystyle{unsrtnat}

### 2018-07-18 paper.tex

--- 2018-07-18 paper.tex
@@
 
+Riga was chosen as the basis fro the geo-located collection, but the demographic in the city (larger proportion of ethinc Russians)  is different than in the rest of the country, especially its Western parts (larger proportion of ethnic Latvians).
+Taking this in the account, our global collection might be less biased that the geo-located one!
+However, it is an open question, whether geo-location of a larger area, for example, by tracking top 10 largest cities, improves the result.
+
+Is it possible to control for bias using the tools described here?
+If we tracked more accounts that tweet dominantly in English, would that introduce other biases?
+Is it possible to select a mixture of topics such that every language would have few topics it dominates?
+How these topics should be explored?
+
 %The challenges of building representative and complete tweet collection are:

### 2018-07-18 paper.tex
Final changes

--- 2018-07-18 paper.tex
@@
 
+\input{figures/uniformity_score.tex}
+
 Latvian is the dominant language: \hl{1\,046\,412 (73.9\%)} tweets are written in it.\footnotemark{} There are \hl{149\,366 (10.5\%)} tweets in Russian, \hl{138\,492 (9.8\%)} in English and \hl{81\,714 (5.8\%)} in other languages.
@@
 Even though the majority is mostly monoligual, this work captured more (at least) bilingual users.
-
-\input{figures/uniformity_score.tex}
 
@@
 
-However, the question of whether the collection is any good remains open.
+%However, the question of whether the collection is any good remains open.
 It would be easy to test its extrinsic properties, for example, whether it leads to improvements in a language identification system when used as training data.

### 2018-07-18 paper.tex
Typos

@@
 Across topics, there is more Latvian content than in the whole collection.
-Among many potential use cases, the corpus can be used, for example, to study the public engagement of major Latvian media outlets and public figures or the factors that determine language choice and content of a tweet.
+Among many potential use cases, the corpus can be used, for example, to study the public engagement of major Latvian media outlets and public figures, or the factors that determine language choice and content of a tweet.
 \end{abstract}
@@
 %
-A tweet collection based on a curated list of users \cite{SANVICENTE16.465,L14-1642} is effective, but extra care must be taken building the list of users.
+A tweet collection based on a curated list of users \cite{SANVICENTE16.465,L14-1642} is effective, but extra care must be taken in building the list of users.
 %
@@
 Following \cite{milajevs:2017:BUCC}, the \texttt{locations} parameter was set to the bounding box of Riga, the capital of Latvia.
-It is small enought to fit into Twitter API restrictions and covers about 40\% of the popilation of Latvia.\footnotemark{}
+It is small enough to fit into Twitter API restrictions and covers about 40\% of the popilation of Latvia.\footnotemark{}
 %
@@
 The collection was manually searched using keywords to get relevant tweets.
-To compensate rich morphology in Latvian and Russian, keywords were manually stemmed.
+To compensate for rich morphology in Latvian and Russian, keywords were manually stemmed.
 For example, \texttt{hokej} was used instead of Latvian \textit{hokejs} to search for the tweets about ice hockey.
@@
 How many topics should you have?
-Topics exhibit various temporal patterns, refer to Figure~\ref{fig:topic_timeline}.
+Topics exhibit various temporal patterns, as seen in Figure~\ref{fig:topic_timeline}.
 The volume of tweets is constant for long-lasting news stories such as the centennial celebration, the refugee crisis, Brexit and ice hockey.
@@
 Tweets in Latvian peak during Advent and Christmas in December, tweets in Russian reach maximum both in December and early January when Orthodox Christmas are celebrated.
-It is worth noting that during the discussion whether Orthodox Christmas should be a public holiday, it sometimes was referred as ``Russian Christmas.'' In spring 2018, there was a discussion to make November 11 a public holiday, thus a spike in activity.
+It is worth noting that during the discussion about whether Orthodox Christmas should be a public holiday, it sometimes was referred as ``Russian Christmas.'' In spring 2018, there was a discussion to make November 11 a public holiday, thus a spike in activity.
 Other event-related topics (May 4, May 8-9, etc.) behave similarly: their activity peaks during the event.
@@
 From the sociolinguistic perspective, instead of avoiding collection artifacts such as topical bias, one could study what linguistic environment the tweets represent.
-What are the factors determining the language, contents and stance of a tweet.
+What are the factors determining the language, contents and stance of a tweet?
 How do these factors interact?
@@
 
-Collection exploration trough keyword search showed that there is a lot of content on various topics and it should be feasible to run a shared retrieval task based on a multilingual collection from the Baltic region to evaluate retrieval systems and study what factors determine relevance.
+Collection exploration using keyword search showed that there is a lot of content on various topics, and it should be feasible to run a shared retrieval task based on a multilingual collection from the Baltic region to evaluate retrieval systems and study what factors determine relevance.
 

### 2018-07-19 paper.tex
Final tweaks

@@
 
-%However, the question of whether the collection is any good remains open.
+However, the question of whether the collection is any good remains open.
 It would be easy to test its extrinsic properties, for example, whether it leads to improvements in a language identification system when used as training data.

### 2018-07-19 paper.tex
Language

@@
 Our base assumption is that geo-located tweets are a representative and unbiased sample of tweets from Latvia.
-Thus, an objective collection should exhibit similar properties as the geo-located one.
+Thus, an objective collection should exhibit similar properties to the geo-located one.
 The main property we study in this work is the language proportion.
-We hypothesize, that an objectively extended collection should have similar language distribution as the initial.
+We hypothesize, that an objectively extended collection should have similar language distribution as the initial collection.
 
@@
 
-The analysis shows that---despite our attempt---the extended collection is biased toward content in Latvian: proportionally there are more tweets in Latvian in the extended collection than in geo-located.
+The analysis shows that---despite our attempt---the extended collection is biased toward content in Latvian: proportionally there are more tweets in Latvian in the extended collection than in the geo-located one.
 We observe this phenomena not only at the ``global level'' (the whole collection), but also at the ``local level'' (across the topics).
@@
 Following \cite{milajevs:2017:BUCC}, the \texttt{locations} parameter was set to the bounding box of Riga, the capital of Latvia.
-It is small enough to fit into Twitter API restrictions and covers about 40\% of the popilation of Latvia.\footnotemark{}
+It is small enough to fit into Twitter API restrictions and covers about 40\% of the population of Latvia.\footnotemark{}
 %
@@
 
-To comply with Twitter's terms of service, on \hl{16 July 2018}, the raw tweet data was redownloaded to get rid of deleted tweets.
+To comply with Twitter's terms of service, on \hl{16 July 2018}, the raw tweet data was re-downloaded to get rid of deleted tweets.
 The tweets that originated a retweet were added to the collection.
-Also, we have noticed a large number of tweets that came from Sweden (probably because of the imprecise \texttt{locations} parameter value), so the tweets which location country code was \texttt{SE} were omitted.
+Also, we noticed a large number of tweets that came from Sweden (probably because of the imprecise \texttt{locations} parameter value), so the tweets with the location country code \texttt{SE} were omitted.
 This resulted in \hl{1\,415\,984} tweets that formed the final collection presented here.\footnotemark{}
@@
 \item \texttt{LV014:} \textbf{March 16} \ Remembrance Day of the Latvian legionnaires.\footnotemark{}
-\item \texttt{LV015:} \textbf{The Chronicles of Melanie} \ Mel\=anijas Hronika (The Chronicles of Melanie) is a Latvian movie that was selected for the Foreign-Language Category for Oscars.
-\item \texttt{LV006:} \textbf{Blizzard of Souls} \ A Latvian movie Dv\=ese\c{l}u Putenis (Blizzard of Souls) that is in production by the time of writing.
+\item \texttt{LV015:} \textbf{The Chronicles of Melanie} \ Mel\=anijas Hronika (The Chronicles of Melanie) is a Latvian movie that was selected for the Foreign-Language Category for the Oscars.
+\item \texttt{LV016:} \textbf{Blizzard of Souls} \ A Latvian movie Dv\=ese\c{l}u Putenis (Blizzard of Souls) that is in production by the time of writing.
 \end{itemize}
